R script for:
Transgenerational effects of maternal obesogenic diet on appetite: a meta-analysis  
========================================================

Step 3 - Bayesian models runs and results  
-----------------------------------------

```{r start, echo=FALSE, message=FALSE, eval=TRUE, include=FALSE}
options(scipen=100)
#getRversion() #3.1.1

install.packages(c("ProjectTemplate", "knitr", "MCMCglmm", "metafor", "rmeta", "meta", "xtable",  "arm", "ade4", "psych","orthopolynom"))
library('ProjectTemplate')
load.project()
#project.info$data
library(MCMCglmm)
library(knitr)
```


Create chow diet subset.
```{r chow diets subset, echo=FALSE, eval=TRUE, include=FALSE}
load("data.RData")
#create chow diet (no-choice) data subset
data_chow <- data[data$Dam_choice_diet == "0",] #69 ES
#data_chow <- subset(data_chow, Dam_choice_diet=="0")
#data_chow68 <- subset(data_chow, Offspr_sex!="FM") #68 ES - for analyses with offspring sex moderator!
data_NC <- subset(data_chow, Offspr_sex!="FM") #68 ES - for analyses with offspring sex moderator!
#write.csv(data_chow,"NM_overfeeding_NCsubset.csv")
#data_chow <- read.csv("NM_overfeeding_NCsubset.csv")
```


### MCMCglmm

Use strains not species as random effect, because there are 8 strains but only 2 species .
We will run a separate model with strains as fixed effects.


Allometrically adjusted food intake - RelIntake2 (RI2)
-----------------------------------------------------

Define full dataset variables.
```{r RI2 full data, echo=FALSE, eval=TRUE, include=FALSE}
d <- data$RelIntake2_Hd
vofd <- data$RelIntake2_Hd_Var_adj
m <- RelIntake2_matrix
AinvG <- solve(m)
AnivG <- as(AinvG,"dgCMatrix")
```

# RI2 - Null model for the full data set.

Run models.
```{r null model RI2 full data, echo=FALSE, eval=FALSE, include=FALSE}
##test runs - without VCV matrix
#m0.0<-MCMCglmm(d~1,random=~Study_ID+Strain,family="gaussian",data=data,verbose=T,mev=vofd,nitt=200000,thin=25,burnin=25000,pr=T) #use stronger prior!
#prior1 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=.002),G2=list(V=1,nu=.002))) #inverse-Gamma piror (slightly informative) - the default is non-informative prior
#m0.0 <- MCMCglmm(d~1,random=~Study_ID+Strain,family="gaussian",data=data,verbose=T,mev=vofd,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior1)
#prior2 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=1,alpha.mu=0,alpha.V=1000),G2=list(V=1,nu=1,alpha.mu=0,alpha.V=1000))) # parameter expanded prior (close to non-informative)
#m0.0 <- MCMCglmm(d~1,random=~Study_ID+Strain,family="gaussian",data=data,verbose=T,mev=vofd,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior2)
##test runs - with VCV matrix
#prior3 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=.002),G2=list(V=1,nu=.002),G3=list(V=1,fix=1))) #inverse-Gamma prior with AnivG
#m0.0 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior3)
#m0.0 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
#prior4 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=1,alpha.mu=0,alpha.V=1000),G2=list(V=1,nu=1,alpha.mu=0,alpha.V=1000),G3=list(V=1,fix=1))) #parameter expanded prior with AnivG
#m0.0 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior4)
#summary(m0.0)
#plot(m0.0)


##long runs
prior3 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=.002),G2=list(V=1,nu=.002),G3=list(V=1,fix=1))) #inverse-Gamma prior with AnivG
model_null_RI2_full_1 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_null_RI2_full_2 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_null_RI2_full_3 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
save(model_null_RI2_full_1,model_null_RI2_full_2,model_null_RI2_full_3,file="model_null_RI2_full.RData") 
```

Get results.
```{r null model RI2 full data results, echo=FALSE, eval=TRUE, include=FALSE}
load("model_null_RI2_full.RData")
m1 <- model_null_RI2_full_1
m2 <- model_null_RI2_full_2
m3 <- model_null_RI2_full_3

#check model convergence
gelman.diag(list(m1$Sol[,1],m2$Sol[,1],m3$Sol[,1])) #The shrink factors should be below 1.05
gelman.diag(list(m1$VCV[,c(1,2)],m2$VCV[,c(1,2)],m3$VCV[,c(1,2)]))
gelman.diag(list(m1$Deviance,m2$Deviance,m3$Deviance))
#check chain autocorrelation
autocorr(m1$Sol[,c(4)])
autocorr(m1$VCV[,c(1:2)])
autocorr(m2$Sol[,c(4)])
autocorr(m2$VCV[,c(1:2)])
autocorr(m3$Sol[,c(4)])
autocorr(m3$VCV[,c(1:2)])
#extract and summarise DIC
print(c(m1$DIC,m2$DIC,m3$DIC))
mean(c(m1$DIC, m2$DIC, m3$DIC)) 
range(c(m1$DIC, m2$DIC, m3$DIC))  

chosen <- m3

plot(chosen)
summary(chosen)

### heterogeneity and variances
WI <- na.omit(1/data$RelIntake2_Hd_Var_adj) 
s2I <- sum(WI*(length(WI)-1))/(sum(WI)^2-sum(WI^2)) # typical sampling (measurement) error variance (sigma2m)
total_var <- chosen$VCV[,"Study_ID"]+chosen$VCV[,"Strain"]+chosen$VCV[,"units"]+s2I # total variance (sigma2t)
total_het <- (total_var-s2I)/total_var # total heterogeneity I2
#for pasting into Excel table
Study_ID <- round(c(summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Study_ID"]/total_var)*100),1)
Strain <- round(c(summary(chosen$VCV[,"Strain"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Strain"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Strain"]/total_var)*100),1)
units <- round(c(summary(chosen$VCV[,"units"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"units"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"units"]/total_var)*100),1)
total <- round(c(summary(total_het)$statistics[1]*100,summary(total_het)$statistics[2]*100,posterior.mode(total_het)*100),1)
res_df <- t(data.frame(Study_ID=Study_ID,Strain=Strain,units=units,total=total))
# version with mean and range for DIC
res_df<-format(res_df, nsmall = 2)
DICs <- c(m1$DIC, m2$DIC, m3$DIC)
DICmean <- format(round(mean(DICs),2), nsmall = 2)
DICrange <- paste0(format(round(range(DICs)[1],2), nsmall = 2)," - ",format(round(range(DICs)[2],2), nsmall = 2))
res_df <- t(c(paste0(DICmean, "(", DICrange, ")"),
            paste0(res_df[1,1],"(",res_df[1,2],")[",res_df[1,3],"]"),
            paste0(res_df[2,1],"(",res_df[2,2],")[",res_df[2,3],"]"),
            paste0(res_df[3,1],"(",res_df[3,2],")[",res_df[3,3],"]"),
            paste0(res_df[4,1],"(",res_df[4,2],")[",res_df[4,3],"]")))
colnames(res_df) <- c("DIC (DIC range)","I2study","I2strain","I2residual","I2total")
rownames(res_df) <- "mean(SD)[mode]"
write.csv(res_df,"results_table_model_null_RI2_full.csv")

### fixed effects (overall intercept)
interc <- c(posterior.mode(chosen$Sol[,1]),summary(chosen$Sol[,1])$statistics[1],summary(chosen$Sol)$statistics[2],HPDinterval(chosen$Sol[,1])[1],HPDinterval(chosen$Sol[,1])[2])
interc <- as.data.frame(t(interc))
rownames(interc) <- c("intercept")
write.table(t(c("Fixed effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_null_RI2_full.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(round(interc,3),"results_table_model_null_RI2_full.csv", sep=",", col.names = FALSE, append = TRUE)

### random effects
Mode <- posterior.mode(chosen$VCV)
Mean <- summary(chosen$VCV)$statistics[,1]
SD <- summary(chosen$VCV)$statistics[,2]
Lower <- HPDinterval(chosen$VCV)[,1]
Upper <- HPDinterval(chosen$VCV)[,2]
res_df <- data.frame(Mode=Mode,Mean=Mean,SD=SD,Lower=Lower,Upper=Upper)
res_df <- res_df[-(dim(res_df)[1]-1),]
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Study_ID","Strain","residuals")
write.table(t(c("Random effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_null_RI2_full.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_null_RI2_full.csv", sep=",", col.names = FALSE, append = TRUE)
```

Table.
```{r null model RI2 full data table, eval=TRUE, echo=FALSE, include=TRUE, message=FALSE, results='asis'}
table <- read.table("results_table_model_null_RI2_full.csv", sep=",")
#table
kable(table, digits = 3)
```

# RI2 - Strain model for the full data set.

Run models.
```{r strain model RI2 full data, echo=FALSE, eval=FALSE, include=FALSE}
prior3s <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=.002),G3=list(V=1,fix=1))) #inverse-Gamma prior with AnivG
#test run
#m0.0<-MCMCglmm(d~Strain-1,random=~Study_ID+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior3s)
#summary(m0.0)
#long runs
model_strain_RI2_full_1 <- MCMCglmm(d~Strain-1,random=~Study_ID+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3s)
model_strain_RI2_full_2 <- MCMCglmm(d~Strain-1,random=~Study_ID+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3s)
model_strain_RI2_full_3 <- MCMCglmm(d~Strain-1,random=~Study_ID+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3s)
save(model_strain_RI2_full_1,model_strain_RI2_full_2,model_strain_RI2_full_3,file="model_strain_RI2_full.RData") 
```

Get results.
```{r strain model RI2 full data results, echo=FALSE, eval=TRUE, include=FALSE}
load("model_strain_RI2_full.RData")
m1 <- model_strain_RI2_full_1
m2 <- model_strain_RI2_full_2
m3 <- model_strain_RI2_full_3

#check model convergence
gelman.diag(list(m1$Sol[,1],m2$Sol[,1],m3$Sol[,1])) #The shrink factors should be below 1.05
gelman.diag(list(m1$VCV[,c(1,3)],m2$VCV[,c(1,3)],m3$VCV[,c(1,3)])) 
gelman.diag(list(m1$Deviance,m2$Deviance,m3$Deviance))
#check chain autocorrelation
autocorr(m1$Sol[,c(2)])
autocorr(m1$VCV[,c(1)])
autocorr(m2$Sol[,c(2)])
autocorr(m2$VCV[,c(1)])
autocorr(m3$Sol[,c(2)])
autocorr(m3$VCV[,c(1)])
#extract and summarise DIC
print(c(m1$DIC,m2$DIC,m3$DIC))
mean(c(m1$DIC, m2$DIC, m3$DIC)) 
range(c(m1$DIC, m2$DIC, m3$DIC))  

chosen <- m1

plot(chosen)
summary(chosen)

### heterogeneity and variances
WI <- na.omit(1/data$RelIntake2_Hd_Var_adj) 
s2I <- sum(WI*(length(WI)-1))/(sum(WI)^2-sum(WI^2)) # typical sampling (measurement) error variance (sigma2m)
total_var <- chosen$VCV[,"Study_ID"]+chosen$VCV[,"units"]+s2I # total variance (sigma2t)
total_het <- (total_var-s2I)/total_var # total heterogeneity I2
#for pasting into Excel table
Study_ID <- round(c(summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Study_ID"]/total_var)*100),1)
units <- round(c(summary(chosen$VCV[,"units"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"units"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"units"]/total_var)*100),1)
total <- round(c(summary(total_het)$statistics[1]*100,summary(total_het)$statistics[2]*100,posterior.mode(total_het)*100),1)
res_df <- t(data.frame(Study_ID=Study_ID,units=units,total=total))
# version with mean and range for DIC
res_df <- format(res_df, nsmall = 2)
DICs <- c(m1$DIC, m2$DIC, m3$DIC)
DICmean <- format(round(mean(DICs),2), nsmall = 2)
DICrange <- paste0(format(round(range(DICs)[1],2), nsmall = 2)," - ",format(round(range(DICs)[2],2), nsmall = 2))
res_df <- t(c(paste0(DICmean, "(", DICrange, ")"),
            paste0(res_df[1,1],"(",res_df[1,2],")[",res_df[1,3],"]"),
            paste0(res_df[2,1],"(",res_df[2,2],")[",res_df[2,3],"]"),
            paste0(res_df[3,1],"(",res_df[3,2],")[",res_df[3,3],"]"), " "))
colnames(res_df) <- c("DIC (DIC range)","I2study","I2residual","I2total", " ")
rownames(res_df) <- "mean(SD)[mode]"
write.csv(res_df,"results_table_model_strain_RI2_full.csv")

### fixed effects (8 strains)
#posterior.mode(chosen$Sol)[1:8]  
#summary(chosen$Sol[,1:8])$statistics[,1]   
#HPDinterval(chosen$Sol[,1:8])
mod <- posterior.mode(chosen$Sol)[1:8]
av <- summary(chosen$Sol[,1:8])$statistics[,1]
sd <- summary(chosen$Sol[,1:8])$statistics[,2]
HPDlo <- HPDinterval(chosen$Sol[,1:8])[,1]
HPDhi <- HPDinterval(chosen$Sol[,1:8])[,2]
res_df <- data.frame(Mode=mod,Mean=av,SD=sd,Lower=HPDlo,Upper=HPDhi)
res_df <- res_df[c(7,8,5,1,2,4,3,6),] #reorder strains
res_df <- round(res_df,3)
rownames(res_df) <- c("rat Sprague-Dawley","rat Wistar","rat Long-Evans","mouse C57BL/6","mouse C57BL/6J","mouse ICR","mouse FVB","mouse NMRI" )
write.table(t(c("Fixed effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_strain_RI2_full.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_strain_RI2_full.csv", sep=",", col.names = FALSE, append = TRUE)

# random effects
#posterior.mode(chosen$VCV) #mode
#summary(chosen$VCV) #mean, SD
#HPDinterval(chosen$VCV) #HPD interval
Mode <- posterior.mode(chosen$VCV)
Mean <- summary(chosen$VCV)$statistics[,1]
SD <- summary(chosen$VCV)$statistics[,2]
Lower <- HPDinterval(chosen$VCV)[,1]
Upper <- HPDinterval(chosen$VCV)[,2]
res_df <- data.frame(Mode=Mode,Mean=Mean,SD=SD,Lower=Lower,Upper=Upper)
res_df <- res_df[-(dim(res_df)[1]-1),]
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Study_ID","residuals")
write.table(t(c("Random effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_strain_RI2_full.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_strain_RI2_full.csv", sep=",", col.names = FALSE, append = TRUE)
```

Table.
```{r strain model RI2 full data table, eval=TRUE, echo=FALSE, include=TRUE, message=FALSE, results='asis'}
table <- read.table("results_table_model_strain_RI2_full.csv", sep=",")
#table
kable(table, digits = 3)
```

# RI2 - full1 model for the full data set (with diet stat and end dates)

Run models.
```{r full1 model RI2 full data, echo=FALSE, eval=FALSE, include=FALSE}
prior3 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=.002),G2=list(V=1,nu=.002),G3=list(V=1,fix=1))) #inverse-Gamma prior with AnivG

#test run
#m0.0 <- MCMCglmm(d~factor(Offspr_sex)+factor(Dam_choice_diet)+Z_Dam_diet_start+Z_Dam_diet_end+Z_Offspr_diet_E+Z_Offspr_diet_PNP_kcal+Z_Intake_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior3)
#summary(m0.0)

#long runs
model_full1_RI2_full_1 <- MCMCglmm(d~factor(Offspr_sex)+factor(Dam_choice_diet)+Z_Dam_diet_start+Z_Dam_diet_end+Z_Offspr_diet_E+Z_Offspr_diet_PNP_kcal+Z_Intake_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_full1_RI2_full_2 <- MCMCglmm(d~factor(Offspr_sex)+factor(Dam_choice_diet)+Z_Dam_diet_start+Z_Dam_diet_end+Z_Offspr_diet_E+Z_Offspr_diet_PNP_kcal+Z_Intake_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_full1_RI2_full_3 <- MCMCglmm(d~factor(Offspr_sex)+factor(Dam_choice_diet)+Z_Dam_diet_start+Z_Dam_diet_end+Z_Offspr_diet_E+Z_Offspr_diet_PNP_kcal+Z_Intake_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
save(model_full1_RI2_full_1,model_full1_RI2_full_2,model_full1_RI2_full_3,file="model_full1_RI2_full.RData") 
```

Get results.
```{r full1 model RI2 full data results, echo=FALSE, eval=TRUE, include=FALSE}
load("model_full1_RI2_full.RData")
m1 <- model_full1_RI2_full_1
m2 <- model_full1_RI2_full_2
m3 <- model_full1_RI2_full_3

gelman.diag(list(m1$Sol[,1],m2$Sol[,1],m3$Sol[,1])) #The shrink factors should be below 1.05
gelman.diag(list(m1$VCV[,c(1,2)],m2$VCV[,c(1,2)],m3$VCV[,c(1,2)]))
gelman.diag(list(m1$Deviance,m2$Deviance,m3$Deviance))
#check chain autocorrelation
autocorr(m1$Sol[,c(4)])
autocorr(m1$VCV[,c(1:2)])
autocorr(m2$Sol[,c(4)])
autocorr(m2$VCV[,c(1:2)])
autocorr(m3$Sol[,c(4)])
autocorr(m3$VCV[,c(1:2)])
#extract and summarise DIC
print(c(m1$DIC,m2$DIC,m3$DIC))
mean(c(m1$DIC, m2$DIC, m3$DIC)) 
range(c(m1$DIC, m2$DIC, m3$DIC))  

chosen <- m1

plot(chosen)
summary(chosen)

### heterogeneity and variances
WI <- na.omit(1/data$RelIntake2_Hd_Var_adj) 
s2I <- sum(WI*(length(WI)-1))/(sum(WI)^2-sum(WI^2)) # typical sampling (measurement) error variance (sigma2m)
total_var <- chosen$VCV[,"Study_ID"]+chosen$VCV[,"Strain"]+chosen$VCV[,"units"]+s2I # total variance (sigma2t)
total_het <- (total_var-s2I)/total_var # total heterogeneity I2
#for pasting into Excel table
Study_ID <- round(c(summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Study_ID"]/total_var)*100),1)
Strain <- round(c(summary(chosen$VCV[,"Strain"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Strain"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Strain"]/total_var)*100),1)
units <- round(c(summary(chosen$VCV[,"units"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"units"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"units"]/total_var)*100),1)
total <- round(c(summary(total_het)$statistics[1]*100,summary(total_het)$statistics[2]*100,posterior.mode(total_het)*100),1)
res_df <- t(data.frame(Study_ID=Study_ID,Strain=Strain,units=units,total=total))
# version with mean and range for DIC
res_df <- format(res_df, nsmall = 2)
DICs <- c(m1$DIC, m2$DIC, m3$DIC)
DICmean <- format(round(mean(DICs),2), nsmall = 2)
DICrange <- paste0(format(round(range(DICs)[1],2), nsmall = 2)," - ",format(round(range(DICs)[2],2), nsmall = 2))
res_df <- t(c(paste0(DICmean, "(", DICrange, ")"),
            paste0(res_df[1,1],"(",res_df[1,2],")[",res_df[1,3],"]"),
            paste0(res_df[2,1],"(",res_df[2,2],")[",res_df[2,3],"]"),
            paste0(res_df[3,1],"(",res_df[3,2],")[",res_df[3,3],"]"),
            paste0(res_df[4,1],"(",res_df[4,2],")[",res_df[4,3],"]")))
colnames(res_df) <- c("DIC (DIC range)","I2study","I2strain","I2residual","I2total")
rownames(res_df) <- "mean(SD)[mode]"
write.csv(res_df,"results_table_model_full1_RI2_full.csv")

### fixed effects (moderators)
#posterior.mode(chosen$Sol)[1:9]  
#summary(chosen$Sol[,1:9])$statistics[,1]   
#HPDinterval(chosen$Sol[,1:9])
mod <- posterior.mode(chosen$Sol)[1:9]
av <- summary(chosen$Sol[,1:9])$statistics[,1]
sd <- summary(chosen$Sol[,1:9])$statistics[,2]
HPDlo <- HPDinterval(chosen$Sol[,1:9])[,1]
HPDhi <- HPDinterval(chosen$Sol[,1:9])[,2]
res_df <- data.frame(Mode=mod,Mean=av,SD=sd,Lower=HPDlo,Upper=HPDhi)
res_df <- res_df[c(1,3,2,4,5,6,7,8,9),] #reorder moderators
#res_df <- res_df[-(dim(res_df)[1]-1),]
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Offspr. female (interc.)","Offspr. male (interc.)","Offspr. both sex (interc.)","Choice-chow dam diet (diff.)","Dam diet start time","Dam diet end time","Offspr. diet E","Offspr diet P:NP","Offspr. age" )
write.table(t(c("Fixed effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_full1_RI2_full.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_full1_RI2_full.csv", sep=",", col.names = FALSE, append = TRUE)

### random effects
Mode <- posterior.mode(chosen$VCV)
Mean <- summary(chosen$VCV)$statistics[,1]
SD <- summary(chosen$VCV)$statistics[,2]
Lower <- HPDinterval(chosen$VCV)[,1]
Upper <- HPDinterval(chosen$VCV)[,2]
res_df <- data.frame(Mode=Mode,Mean=Mean,SD=SD,Lower=Lower,Upper=Upper)
res_df <- res_df[-3,]
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Study_ID","Strain","residuals")
write.table(t(c("Random effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_full1_RI2_full.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_full1_RI2_full.csv", sep=",", col.names = FALSE, append = TRUE)
```

Table.
```{r full1 model RI2 full data table, eval=TRUE, echo=FALSE, include=TRUE, message=FALSE, results='asis'}
table <- read.table("results_table_model_full1_RI2_full.csv", sep=",")
#table
kable(table, digits = 3)
```


# RI2 - full2 model for the full data set (timing of the diet as categorical variable: lactation included or not)

Run models.
```{r full2 model RI2 full data, echo=FALSE, eval=FALSE, include=FALSE}
prior3 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=.002),G2=list(V=1,nu=.002),G3=list(V=1,fix=1))) #inverse-Gamma prior with AnivG

#test run
#m0.0 <- MCMCglmm(d~factor(Offspr_sex)+factor(Dam_choice_diet)+factor(Dam_diet_lactation_incl)+Z_Offspr_diet_E+Z_Offspr_diet_PNP_kcal+Z_Intake_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior3)
#summary(m0.0)

#long runs
model_full2_RI2_full_1 <- MCMCglmm(d~factor(Offspr_sex)+factor(Dam_choice_diet)+factor(Dam_diet_lactation_incl)+Z_Offspr_diet_E+Z_Offspr_diet_PNP_kcal+Z_Intake_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_full2_RI2_full_2 <- MCMCglmm(d~factor(Offspr_sex)+factor(Dam_choice_diet)+factor(Dam_diet_lactation_incl)+Z_Offspr_diet_E+Z_Offspr_diet_PNP_kcal+Z_Intake_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_full2_RI2_full_3 <- MCMCglmm(d~factor(Offspr_sex)+factor(Dam_choice_diet)+factor(Dam_diet_lactation_incl)+Z_Offspr_diet_E+Z_Offspr_diet_PNP_kcal+Z_Intake_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
save(model_full2_RI2_full_1,model_full2_RI2_full_2,model_full2_RI2_full_3,file="model_full2_RI2_full.RData") 
```

Get results.
```{r full2 model RI2 full data results, echo=FALSE, eval=TRUE, include=FALSE}
load("model_full2_RI2_full.RData")
m1 <- model_full2_RI2_full_1
m2 <- model_full2_RI2_full_2
m3 <- model_full2_RI2_full_3

gelman.diag(list(m1$Sol[,1],m2$Sol[,1],m3$Sol[,1])) #The shrink factors should be below 1.05
gelman.diag(list(m1$VCV[,c(1,2)],m2$VCV[,c(1,2)],m3$VCV[,c(1,2)]))
gelman.diag(list(m1$Deviance,m2$Deviance,m3$Deviance))
#check chain autocorrelation
autocorr(m1$Sol[,c(4)])
autocorr(m1$VCV[,c(1:2)])
autocorr(m2$Sol[,c(4)])
autocorr(m2$VCV[,c(1:2)])
autocorr(m3$Sol[,c(4)])
autocorr(m3$VCV[,c(1:2)])
#extract and summarise DIC
print(c(m1$DIC,m2$DIC,m3$DIC))
mean(c(m1$DIC, m2$DIC, m3$DIC)) 
range(c(m1$DIC, m2$DIC, m3$DIC))  

chosen <- m3

plot(chosen)
summary(chosen)

### heterogeneity and variances
WI <- na.omit(1/data$RelIntake2_Hd_Var_adj) 
s2I <- sum(WI*(length(WI)-1))/(sum(WI)^2-sum(WI^2)) # typical sampling (measurement) error variance (sigma2m)
total_var <- chosen$VCV[,"Study_ID"]+chosen$VCV[,"Strain"]+chosen$VCV[,"units"]+s2I # total variance (sigma2t)
total_het <- (total_var-s2I)/total_var # total heterogeneity I2
#for pasting into Excel table
Study_ID <- round(c(summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Study_ID"]/total_var)*100),1)
Strain <- round(c(summary(chosen$VCV[,"Strain"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Strain"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Strain"]/total_var)*100),1)
units <- round(c(summary(chosen$VCV[,"units"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"units"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"units"]/total_var)*100),1)
total <- round(c(summary(total_het)$statistics[1]*100,summary(total_het)$statistics[2]*100,posterior.mode(total_het)*100),1)
res_df <- t(data.frame(Study_ID=Study_ID,Strain=Strain,units=units,total=total))
# version with mean and range for DIC
res_df <- format(res_df, nsmall = 2)
DICs <- c(m1$DIC, m2$DIC, m3$DIC)
DICmean <- format(round(mean(DICs),2), nsmall = 2)
DICrange <- paste0(format(round(range(DICs)[1],2), nsmall = 2)," - ",format(round(range(DICs)[2],2), nsmall = 2))
res_df <- t(c(paste0(DICmean, "(", DICrange, ")"),
            paste0(res_df[1,1],"(",res_df[1,2],")[",res_df[1,3],"]"),
            paste0(res_df[2,1],"(",res_df[2,2],")[",res_df[2,3],"]"),
            paste0(res_df[3,1],"(",res_df[3,2],")[",res_df[3,3],"]"),
            paste0(res_df[4,1],"(",res_df[4,2],")[",res_df[4,3],"]")))
colnames(res_df) <- c("DIC (DIC range)","I2study","I2strain","I2residual","I2total")
rownames(res_df) <- "mean(SD)[mode]"
write.csv(res_df,"results_table_model_full2_RI2_full.csv")

### fixed effects (moderators)
#posterior.mode(chosen$Sol)[1:8]  
#summary(chosen$Sol[,1:8])$statistics[,1]   
#HPDinterval(chosen$Sol[,1:8])
mod <- posterior.mode(chosen$Sol)[1:8]
av <- summary(chosen$Sol[,1:8])$statistics[,1]
sd <- summary(chosen$Sol[,1:8])$statistics[,2]
HPDlo <- HPDinterval(chosen$Sol[,1:8])[,1]
HPDhi <- HPDinterval(chosen$Sol[,1:8])[,2]
res_df <- data.frame(Mode=mod,Mean=av,SD=sd,Lower=HPDlo,Upper=HPDhi)
res_df <- res_df[c(1,3,2,4:8),] #reorder moderators
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Offspr. female (interc.)","Offspr. male (interc.)","Offspr. both sex (interc.)","Choice-chow dam diet (diff.)","Dam diet during lactation (diff.)","Offspr. diet E","Offspr diet P:NP","Offspr. age" )
write.table(t(c("Fixed effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_full2_RI2_full.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_full2_RI2_full.csv", sep=",", col.names = FALSE, append = TRUE)

### random effects
Mode <- posterior.mode(chosen$VCV)
Mean <- summary(chosen$VCV)$statistics[,1]
SD <- summary(chosen$VCV)$statistics[,2]
Lower <- HPDinterval(chosen$VCV)[,1]
Upper <- HPDinterval(chosen$VCV)[,2]
res_df <- data.frame(Mode=Mode,Mean=Mean,SD=SD,Lower=Lower,Upper=Upper)
res_df <- res_df[-3,]
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Study_ID","Strain","residuals")
write.table(t(c("Random effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_full2_RI2_full.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_full2_RI2_full.csv", sep=",", col.names = FALSE, append = TRUE)
```

Table.
```{r full2 model RI2 full data table, eval=TRUE, echo=FALSE, include=TRUE, message=FALSE, results='asis'}
table <- read.table("results_table_model_full2_RI2_full.csv", sep=",")
#table
kable(table, digits = 3)
```


# RI2 - Null model for the chow data subset.

Define chow data subset variables.
```{r RI2 chow data, echo=FALSE, eval=TRUE, include=FALSE}
d <- data_NC$RelIntake2_Hd
vofd <- data_NC$RelIntake2_Hd_Var_adj
m_NC <- Bodyweight_matrix_NC
AinvG_NC <- solve(m_NC)
AnivG_NC <- as(AinvG_NC,"dgCMatrix")
```

Run models.
```{r null model RI2 chow data, echo=FALSE, eval=FALSE, include=FALSE}
##test runs - with VCV matrix
#prior3 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=.002),G2=list(V=1,nu=.002),G3=list(V=1,fix=1))) #inverse-Gamma prior with AnivG
#m0.0 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior3)
#m0.0 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
#prior4 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=1,alpha.mu=0,alpha.V=1000),G2=list(V=1,nu=1,alpha.mu=0,alpha.V=1000),G3=list(V=1,fix=1))) #parameter expanded prior with AnivG
#m0.0 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior4)
#summary(m0.0)
#plot(m0.0)

##long runs
prior3 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=.002),G2=list(V=1,nu=.002),G3=list(V=1,fix=1))) #inverse-Gamma prior with AnivG
model_null_RI2_chow_1 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_null_RI2_chow_2 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_null_RI2_chow_3 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)

save(model_null_RI2_chow_1,model_null_RI2_chow_2,model_null_RI2_chow_3,file="model_null_RI2_chow.RData") 
```

Get results.
```{r null model RI2 chow data results, echo=FALSE, eval=TRUE, include=FALSE}
load("model_null_RI2_chow.RData")
m1 <- model_null_RI2_chow_1
m2 <- model_null_RI2_chow_2
m3 <- model_null_RI2_chow_3

#check model convergence
gelman.diag(list(m1$Sol[,1],m2$Sol[,1],m3$Sol[,1])) #The shrink factors should be below 1.05
gelman.diag(list(m1$VCV[,c(1,2)],m2$VCV[,c(1,2)],m3$VCV[,c(1,2)]))
gelman.diag(list(m1$Deviance,m2$Deviance,m3$Deviance))
#check chain autocorrelation
autocorr(m1$Sol[,c(4)])
autocorr(m1$VCV[,c(1:2)])
autocorr(m2$Sol[,c(4)])
autocorr(m2$VCV[,c(1:2)])
autocorr(m3$Sol[,c(4)])
autocorr(m3$VCV[,c(1:2)])
#extract and summarise DIC
print(c(m1$DIC,m2$DIC,m3$DIC))
mean(c(m1$DIC, m2$DIC, m3$DIC)) 
range(c(m1$DIC, m2$DIC, m3$DIC))  

chosen <- m2

plot(chosen)
summary(chosen)

### heterogeneity and variances
WI <- na.omit(1/data_NC$RelIntake2_Hd_Var_adj) 
s2I <- sum(WI*(length(WI)-1))/(sum(WI)^2-sum(WI^2)) # typical sampling (measurement) error variance (sigma2m)
total_var <- chosen$VCV[,"Study_ID"]+chosen$VCV[,"Strain"]+chosen$VCV[,"units"]+s2I # total variance (sigma2t)
total_het <- (total_var-s2I)/total_var # total heterogeneity I2
#for pasting into Excel table
Study_ID <- round(c(summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Study_ID"]/total_var)*100),1)
Strain <- round(c(summary(chosen$VCV[,"Strain"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Strain"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Strain"]/total_var)*100),1)
units <- round(c(summary(chosen$VCV[,"units"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"units"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"units"]/total_var)*100),1)
total <- round(c(summary(total_het)$statistics[1]*100,summary(total_het)$statistics[2]*100,posterior.mode(total_het)*100),1)
res_df <- t(data.frame(Study_ID=Study_ID,Strain=Strain,units=units,total=total))
# version with mean and range for DIC
res_df <- format(res_df, nsmall = 2)
DICs <- c(m1$DIC, m2$DIC, m3$DIC)
DICmean <- format(round(mean(DICs),2), nsmall = 2)
DICrange <- paste0(format(round(range(DICs)[1],2), nsmall = 2)," - ",format(round(range(DICs)[2],2), nsmall = 2))
res_df <- t(c(paste0(DICmean, "(", DICrange, ")"),
            paste0(res_df[1,1],"(",res_df[1,2],")[",res_df[1,3],"]"),
            paste0(res_df[2,1],"(",res_df[2,2],")[",res_df[2,3],"]"),
            paste0(res_df[3,1],"(",res_df[3,2],")[",res_df[3,3],"]"),
            paste0(res_df[4,1],"(",res_df[4,2],")[",res_df[4,3],"]")))
colnames(res_df) <- c("DIC (DIC range)","I2study","I2strain","I2residual","I2total")
rownames(res_df) <- "mean(SD)[mode]"
write.csv(res_df,"results_table_model_null_RI2_chow.csv")

### fixed effects (overall intercept)
interc <- c(posterior.mode(chosen$Sol[,1]),summary(chosen$Sol[,1])$statistics[1],summary(chosen$Sol)$statistics[2],HPDinterval(chosen$Sol[,1])[1],HPDinterval(chosen$Sol[,1])[2])
interc <- as.data.frame(t(interc))
rownames(interc) <- c("intercept")
write.table(t(c("Fixed effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_null_RI2_chow.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(round(interc,3),"results_table_model_null_RI2_chow.csv", sep=",", col.names = FALSE, append = TRUE)

### random effects
Mode <- posterior.mode(chosen$VCV)
Mean <- summary(chosen$VCV)$statistics[,1]
SD <- summary(chosen$VCV)$statistics[,2]
Lower <- HPDinterval(chosen$VCV)[,1]
Upper <- HPDinterval(chosen$VCV)[,2]
res_df <- data.frame(Mode=Mode,Mean=Mean,SD=SD,Lower=Lower,Upper=Upper)
res_df <- res_df[-(dim(res_df)[1]-1),]
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Study_ID","Strain","residuals")
write.table(t(c("Random effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_null_RI2_chow.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_null_RI2_chow.csv", sep=",", col.names = FALSE, append = TRUE)
```

Table.
```{r null model RI2 chow data table, eval=TRUE, echo=FALSE, include=TRUE, message=FALSE, results='asis'}
table <- read.table("results_table_model_null_RI2_chow.csv", sep=",")
#table
kable(table, digits = 3)
```

# RI2 - Strain model for the chow data subset.

Run models.
```{r strain model RI2 chow data, echo=FALSE, eval=FALSE, include=FALSE}
prior3s <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=.002),G3=list(V=1,fix=1))) #inverse-Gamma prior with AnivG

##test runs - with VCV matrix
#m0.0 <- MCMCglmm(d~Strain-1,random=~Study_ID+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior3s)
#m0.0 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
#prior4 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=1,alpha.mu=0,alpha.V=1000),G2=list(V=1,nu=1,alpha.mu=0,alpha.V=1000),G3=list(V=1,fix=1))) #parameter expanded prior with AnivG
#m0.0 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior4)
#summary(m0.0)

##long runs
model_strain_RI2_chow_1 <- MCMCglmm(d~Strain-1,random=~Study_ID+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3s)
model_strain_RI2_chow_2 <- MCMCglmm(d~Strain-1,random=~Study_ID+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3s)
model_strain_RI2_chow_3 <- MCMCglmm(d~Strain-1,random=~Study_ID+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3s)
save(model_strain_RI2_chow_1,model_strain_RI2_chow_2,model_strain_RI2_chow_3,file="model_strain_RI2_chow.RData") 
```


Get results.
```{r strain model RI2 chow data results, echo=FALSE, eval=TRUE, include=FALSE}
load("model_strain_RI2_chow.RData")
m1 <- model_strain_RI2_chow_1
m2 <- model_strain_RI2_chow_2
m3 <- model_strain_RI2_chow_3

#check model convergence
gelman.diag(list(m1$Sol[,1],m2$Sol[,1],m3$Sol[,1])) #The shrink factors should be below 1.05
gelman.diag(list(m1$VCV[,c(1,3)],m2$VCV[,c(1,3)],m3$VCV[,c(1,3)])) 
gelman.diag(list(m1$Deviance,m2$Deviance,m3$Deviance))
#check chain autocorrelation
autocorr(m1$Sol[,c(2)])
autocorr(m1$VCV[,c(1)])
autocorr(m2$Sol[,c(2)])
autocorr(m2$VCV[,c(1)])
autocorr(m3$Sol[,c(2)])
autocorr(m3$VCV[,c(1)])
#extract and summarise DIC
print(c(m1$DIC,m2$DIC,m3$DIC))
mean(c(m1$DIC, m2$DIC, m3$DIC)) 
range(c(m1$DIC, m2$DIC, m3$DIC))  

chosen <- m2

plot(chosen)
summary(chosen)

### heterogeneity and variances
WI <- na.omit(1/data_NC$RelIntake2_Hd_Var_adj) 
s2I <- sum(WI*(length(WI)-1))/(sum(WI)^2-sum(WI^2)) # typical sampling (measurement) error variance (sigma2m)
total_var <- chosen$VCV[,"Study_ID"]+chosen$VCV[,"units"]+s2I # total variance (sigma2t)
total_het <- (total_var-s2I)/total_var # total heterogeneity I2
#for pasting into Excel table
Study_ID <- round(c(summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Study_ID"]/total_var)*100),1)
units <- round(c(summary(chosen$VCV[,"units"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"units"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"units"]/total_var)*100),1)
total <- round(c(summary(total_het)$statistics[1]*100,summary(total_het)$statistics[2]*100,posterior.mode(total_het)*100),1)
res_df <- t(data.frame(Study_ID=Study_ID,units=units,total=total))
# version with mean and range for DIC
res_df <- format(res_df, nsmall = 2)
DICs <- c(m1$DIC, m2$DIC, m3$DIC)
DICmean <- format(round(mean(DICs),2), nsmall = 2)
DICrange <- paste0(format(round(range(DICs)[1],2), nsmall = 2)," - ",format(round(range(DICs)[2],2), nsmall = 2))
res_df <- t(c(paste0(DICmean, "(", DICrange, ")"),
            paste0(res_df[1,1],"(",res_df[1,2],")[",res_df[1,3],"]"),
            paste0(res_df[2,1],"(",res_df[2,2],")[",res_df[2,3],"]"),
            paste0(res_df[3,1],"(",res_df[3,2],")[",res_df[3,3],"]"), " "))
colnames(res_df) <- c("DIC (DIC range)","I2study","I2residual","I2total", " ")
rownames(res_df) <- "mean(SD)[mode]"
write.csv(res_df,"results_table_model_strain_RI2_chow.csv")

### fixed effects (8 strains)
#posterior.mode(chosen$Sol)[1:8]  
#summary(chosen$Sol[,1:8])$statistics[,1]   
#HPDinterval(chosen$Sol[,1:8])
mod <- posterior.mode(chosen$Sol)[1:8]
av <- summary(chosen$Sol[,1:8])$statistics[,1]
sd <- summary(chosen$Sol[,1:8])$statistics[,2]
HPDlo <- HPDinterval(chosen$Sol[,1:8])[,1]
HPDhi <- HPDinterval(chosen$Sol[,1:8])[,2]
res_df <- data.frame(Mode=mod,Mean=av,SD=sd,Lower=HPDlo,Upper=HPDhi)
res_df <- res_df[c(7,8,5,1,2,4,3,6),] #reorder strains
res_df <- round(res_df,3)
rownames(res_df) <- c("rat Sprague-Dawley","rat Wistar","rat Long-Evans","mouse C57BL/6","mouse C57BL/6J","mouse ICR","mouse FVB","mouse NMRI" )
write.table(t(c("Fixed effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_strain_RI2_chow.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_strain_RI2_chow.csv", sep=",", col.names = FALSE, append = TRUE)

# random effects
#posterior.mode(chosen$VCV) #mode
#summary(chosen$VCV) #mean, SD
#HPDinterval(chosen$VCV) #HPD interval
Mode <- posterior.mode(chosen$VCV)
Mean <- summary(chosen$VCV)$statistics[,1]
SD <- summary(chosen$VCV)$statistics[,2]
Lower <- HPDinterval(chosen$VCV)[,1]
Upper <- HPDinterval(chosen$VCV)[,2]
res_df <- data.frame(Mode=Mode,Mean=Mean,SD=SD,Lower=Lower,Upper=Upper)
res_df <- res_df[-(dim(res_df)[1]-1),]
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Study_ID","residuals")
write.table(t(c("Random effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_strain_RI2_chow.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_strain_RI2_chow.csv", sep=",", col.names = FALSE, append = TRUE)
```

Table.
```{r strain model RI2 chow data table, eval=TRUE, echo=FALSE, include=TRUE, message=FALSE, results='asis'}
table <- read.table("results_table_model_strain_RI2_chow.csv", sep=",")
#table
kable(table, digits = 3)
```


# RI2 - full1 model for the chow data subset (with diet stat and end dates)

Run models.
```{r full1 model RI2 chow data, echo=FALSE, eval=FALSE, include=FALSE}
prior3 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=.002),G2=list(V=1,nu=.002),G3=list(V=1,fix=1))) #inverse-Gamma prior with AnivG

#test run
#m0.0 <- MCMCglmm(d~factor(Offspr_sex)+Z_Dam_diet_start+Z_Dam_diet_end+Z_Dam_diet_exp_E+Z_Dam_diet_exp_PNP_kcal+Z_Intake_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior3)
#summary(m0.0)

#long runs
model_full1_RI2_chow_1 <- MCMCglmm(d~factor(Offspr_sex)+Z_Dam_diet_start+Z_Dam_diet_end+Z_Dam_diet_exp_E+Z_Dam_diet_exp_PNP_kcal+Z_Intake_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_full1_RI2_chow_2 <- MCMCglmm(d~factor(Offspr_sex)+Z_Dam_diet_start+Z_Dam_diet_end+Z_Dam_diet_exp_E+Z_Dam_diet_exp_PNP_kcal+Z_Intake_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_full1_RI2_chow_3 <- MCMCglmm(d~factor(Offspr_sex)+Z_Dam_diet_start+Z_Dam_diet_end+Z_Dam_diet_exp_E+Z_Dam_diet_exp_PNP_kcal+Z_Intake_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
save(model_full1_RI2_chow_1,model_full1_RI2_chow_2,model_full1_RI2_chow_3,file="model_full1_RI2_chow.RData") 
```


Get results.
```{r full1 model RI2 chow data results, echo=FALSE, eval=TRUE, include=FALSE}
load("model_full1_RI2_chow.RData")
m1 <- model_full1_RI2_chow_1
m2 <- model_full1_RI2_chow_2
m3 <- model_full1_RI2_chow_3

gelman.diag(list(m1$Sol[,1],m2$Sol[,1],m3$Sol[,1])) #The shrink factors should be below 1.05
gelman.diag(list(m1$VCV[,c(1,2)],m2$VCV[,c(1,2)],m3$VCV[,c(1,2)]))
gelman.diag(list(m1$Deviance,m2$Deviance,m3$Deviance))
#check chain autocorrelation
autocorr(m1$Sol[,c(4)])
autocorr(m1$VCV[,c(1:2)])
autocorr(m2$Sol[,c(4)])
autocorr(m2$VCV[,c(1:2)])
autocorr(m3$Sol[,c(4)])
autocorr(m3$VCV[,c(1:2)])
#extract and summarise DIC
print(c(m1$DIC,m2$DIC,m3$DIC))
mean(c(m1$DIC, m2$DIC, m3$DIC)) 
range(c(m1$DIC, m2$DIC, m3$DIC))  

chosen <- m2

plot(chosen)
summary(chosen)

### heterogeneity and variances
WI <- na.omit(1/data_NC$RelIntake2_Hd_Var_adj) 
s2I <- sum(WI*(length(WI)-1))/(sum(WI)^2-sum(WI^2)) # typical sampling (measurement) error variance (sigma2m)
total_var <- chosen$VCV[,"Study_ID"]+chosen$VCV[,"Strain"]+chosen$VCV[,"units"]+s2I # total variance (sigma2t)
total_het <- (total_var-s2I)/total_var # total heterogeneity I2
#for pasting into Excel table
Study_ID <- round(c(summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Study_ID"]/total_var)*100),1)
Strain <- round(c(summary(chosen$VCV[,"Strain"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Strain"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Strain"]/total_var)*100),1)
units <- round(c(summary(chosen$VCV[,"units"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"units"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"units"]/total_var)*100),1)
total <- round(c(summary(total_het)$statistics[1]*100,summary(total_het)$statistics[2]*100,posterior.mode(total_het)*100),1)
res_df <- t(data.frame(Study_ID=Study_ID,Strain=Strain,units=units,total=total))
# version with mean and range for DIC
res_df <- format(res_df, nsmall = 2)
DICs <- c(m1$DIC, m2$DIC, m3$DIC)
DICmean <- format(round(mean(DICs),2), nsmall = 2)
DICrange <- paste0(format(round(range(DICs)[1],2), nsmall = 2)," - ",format(round(range(DICs)[2],2), nsmall = 2))
res_df <- t(c(paste0(DICmean, "(", DICrange, ")"),
            paste0(res_df[1,1],"(",res_df[1,2],")[",res_df[1,3],"]"),
            paste0(res_df[2,1],"(",res_df[2,2],")[",res_df[2,3],"]"),
            paste0(res_df[3,1],"(",res_df[3,2],")[",res_df[3,3],"]"),
            paste0(res_df[4,1],"(",res_df[4,2],")[",res_df[4,3],"]")))
colnames(res_df) <- c("DIC (DIC range)","I2study","I2strain","I2residual","I2total")
rownames(res_df) <- "mean(SD)[mode]"
write.csv(res_df,"results_table_model_full1_RI2_chow.csv")

### fixed effects (moderators)
#posterior.mode(chosen$Sol)[1:7]  
#summary(chosen$Sol[,1:7])$statistics[,1]   
#HPDinterval(chosen$Sol[,1:7])
mod <- posterior.mode(chosen$Sol)[1:7]
av <- summary(chosen$Sol[,1:7])$statistics[,1]
sd <- summary(chosen$Sol[,1:7])$statistics[,2]
HPDlo <- HPDinterval(chosen$Sol[,1:7])[,1]
HPDhi <- HPDinterval(chosen$Sol[,1:7])[,2]
res_df <- data.frame(Mode=mod,Mean=av,SD=sd,Lower=HPDlo,Upper=HPDhi)
#res_df <- res_df[-(dim(res_df)[1]-1),]
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Offspr. female (interc.)","Offspr. male (interc.)","Dam diet start time","Dam diet end time","Dam diet E","Dam diet P:NP","Offspr. age" )
write.table(t(c("Fixed effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_full1_RI2_chow.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_full1_RI2_chow.csv", sep=",", col.names = FALSE, append = TRUE)

### random effects
Mode <- posterior.mode(chosen$VCV)
Mean <- summary(chosen$VCV)$statistics[,1]
SD <- summary(chosen$VCV)$statistics[,2]
Lower <- HPDinterval(chosen$VCV)[,1]
Upper <- HPDinterval(chosen$VCV)[,2]
res_df <- data.frame(Mode=Mode,Mean=Mean,SD=SD,Lower=Lower,Upper=Upper)
res_df <- res_df[-3,]
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Study_ID","Strain","residuals")
write.table(t(c("Random effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_full1_RI2_chow.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_full1_RI2_chow.csv", sep=",", col.names = FALSE, append = TRUE)
```

Table.
```{r full1 model RI2 chow data table, eval=TRUE, echo=FALSE, include=TRUE, message=FALSE, results='asis'}
table <- read.table("results_table_model_full1_RI2_full.csv", sep=",")
#table
kable(table, digits = 3)
```


# RI2 - full2 model for the chow data subset (timing of the diet as categorical variable: lactation included or not)

Run models.
```{r full2 model RI2 chow data, echo=FALSE, eval=FALSE, include=FALSE}
prior3 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=.002),G2=list(V=1,nu=.002),G3=list(V=1,fix=1))) #inverse-Gamma prior with AnivG

#test run
#m0.0 <- MCMCglmm(d~factor(Offspr_sex)+factor(Dam_diet_lactation_incl)+Z_Dam_diet_exp_E+Z_Dam_diet_exp_PNP_kcal+Z_Intake_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior3)
#summary(m0.0)

#long runs
model_full2_RI2_chow_1 <- MCMCglmm(d~factor(Offspr_sex)+factor(Dam_diet_lactation_incl)+Z_Dam_diet_exp_E+Z_Dam_diet_exp_PNP_kcal+Z_Intake_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_full2_RI2_chow_2 <- MCMCglmm(d~factor(Offspr_sex)+factor(Dam_diet_lactation_incl)+Z_Dam_diet_exp_E+Z_Dam_diet_exp_PNP_kcal+Z_Intake_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_full2_RI2_chow_3 <- MCMCglmm(d~factor(Offspr_sex)+factor(Dam_diet_lactation_incl)+Z_Dam_diet_exp_E+Z_Dam_diet_exp_PNP_kcal+Z_Intake_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
save(model_full2_RI2_chow_1,model_full2_RI2_chow_2,model_full2_RI2_chow_3,file="model_full2_RI2_chow.RData") 
```


Get results.
```{r full2 model RI2 chow data results, echo=FALSE, eval=TRUE, include=FALSE}
load("model_full2_RI2_chow.RData")
m1 <- model_full2_RI2_chow_1
m2 <- model_full2_RI2_chow_2
m3 <- model_full2_RI2_chow_3

gelman.diag(list(m1$Sol[,1],m2$Sol[,1],m3$Sol[,1])) #The shrink factors should be below 1.05
gelman.diag(list(m1$VCV[,c(1,2)],m2$VCV[,c(1,2)],m3$VCV[,c(1,2)]))
gelman.diag(list(m1$Deviance,m2$Deviance,m3$Deviance))
#check chain autocorrelation
autocorr(m1$Sol[,c(4)])
autocorr(m1$VCV[,c(1:2)])
autocorr(m2$Sol[,c(4)])
autocorr(m2$VCV[,c(1:2)])
autocorr(m3$Sol[,c(4)])
autocorr(m3$VCV[,c(1:2)])
#extract and summarise DIC
print(c(m1$DIC,m2$DIC,m3$DIC))
mean(c(m1$DIC, m2$DIC, m3$DIC)) 
range(c(m1$DIC, m2$DIC, m3$DIC))  

chosen <- m3

plot(chosen)
summary(chosen)

### heterogeneity and variances
WI <- na.omit(1/data_NC$RelIntake2_Hd_Var_adj) 
s2I <- sum(WI*(length(WI)-1))/(sum(WI)^2-sum(WI^2)) # typical sampling (measurement) error variance (sigma2m)
total_var <- chosen$VCV[,"Study_ID"]+chosen$VCV[,"Strain"]+chosen$VCV[,"units"]+s2I # total variance (sigma2t)
total_het <- (total_var-s2I)/total_var # total heterogeneity I2
#for pasting into Excel table
Study_ID <- round(c(summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Study_ID"]/total_var)*100),1)
Strain <- round(c(summary(chosen$VCV[,"Strain"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Strain"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Strain"]/total_var)*100),1)
units <- round(c(summary(chosen$VCV[,"units"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"units"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"units"]/total_var)*100),1)
total <- round(c(summary(total_het)$statistics[1]*100,summary(total_het)$statistics[2]*100,posterior.mode(total_het)*100),1)
res_df <- t(data.frame(Study_ID=Study_ID,Strain=Strain,units=units,total=total))
# version with mean and range for DIC
res_df <- format(res_df, nsmall = 2)
DICs <- c(m1$DIC, m2$DIC, m3$DIC)
DICmean <- format(round(mean(DICs),2), nsmall = 2)
DICrange <- paste0(format(round(range(DICs)[1],2), nsmall = 2)," - ",format(round(range(DICs)[2],2), nsmall = 2))
res_df <- t(c(paste0(DICmean, "(", DICrange, ")"),
            paste0(res_df[1,1],"(",res_df[1,2],")[",res_df[1,3],"]"),
            paste0(res_df[2,1],"(",res_df[2,2],")[",res_df[2,3],"]"),
            paste0(res_df[3,1],"(",res_df[3,2],")[",res_df[3,3],"]"),
            paste0(res_df[4,1],"(",res_df[4,2],")[",res_df[4,3],"]")))
colnames(res_df) <- c("DIC (DIC range)","I2study","I2strain","I2residual","I2total")
rownames(res_df) <- "mean(SD)[mode]"
write.csv(res_df,"results_table_model_full2_RI2_chow.csv")

### fixed effects (moderators)
#posterior.mode(chosen$Sol)[1:6]  
#summary(chosen$Sol[,1:6])$statistics[,1]   
#HPDinterval(chosen$Sol[,1:6])
mod <- posterior.mode(chosen$Sol)[1:6]
av <- summary(chosen$Sol[,1:6])$statistics[,1]
sd <- summary(chosen$Sol[,1:6])$statistics[,2]
HPDlo <- HPDinterval(chosen$Sol[,1:6])[,1]
HPDhi <- HPDinterval(chosen$Sol[,1:6])[,2]
res_df <- data.frame(Mode=mod,Mean=av,SD=sd,Lower=HPDlo,Upper=HPDhi)
#res_df <- res_df[c(1,3,2,4:6),] #reorder moderators
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Offspr. female (interc.)","Offspr. male (interc.)","Dam diet during lactation (diff.)","Dam diet E","Dam diet P:NP","Offspr. age" )
write.table(t(c("Fixed effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_full2_RI2_chow.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_full2_RI2_chow.csv", sep=",", col.names = FALSE, append = TRUE)

### random effects
Mode <- posterior.mode(chosen$VCV)
Mean <- summary(chosen$VCV)$statistics[,1]
SD <- summary(chosen$VCV)$statistics[,2]
Lower <- HPDinterval(chosen$VCV)[,1]
Upper <- HPDinterval(chosen$VCV)[,2]
res_df <- data.frame(Mode=Mode,Mean=Mean,SD=SD,Lower=Lower,Upper=Upper)
res_df <- res_df[-3,]
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Study_ID","Strain","residuals")
write.table(t(c("Random effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_full2_RI2_chow.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_full2_RI2_chow.csv", sep=",", col.names = FALSE, append = TRUE)
```

Table.
```{r full2 model RI2 chow data table, eval=TRUE, echo=FALSE, include=TRUE, message=FALSE, results='asis'}
table <- read.table("results_table_model_full2_RI2_chow.csv", sep=",")
#table
kable(table, digits = 3)
```



Offspring body weight - Bodyweight (BW)
-----------------------------------------------------

Define full dataset variables.
```{r BW full data, echo=FALSE, eval=TRUE, include=FALSE}
d <- data$Bodyweight_Hd
vofd <- data$Bodyweight_Hd_Var_adj
m <- Bodyweight_matrix
AinvG <- solve(m)
AnivG <- as(AinvG,"dgCMatrix")
```


# BW - Null model for the full data set.

Run models.
```{r null model BW full data, echo=FALSE, eval=FALSE, include=FALSE}
##test runs - without VCV matrix
#m0.0<-MCMCglmm(d~1,random=~Study_ID+Strain,family="gaussian",data=data,verbose=T,mev=vofd,nitt=200000,thin=25,burnin=25000,pr=T) #use stronger prior!
#prior1 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=.002),G2=list(V=1,nu=.002))) #inverse-Gamma piror (slightly informative) - the default is non-informative prior
#m0.0 <- MCMCglmm(d~1,random=~Study_ID+Strain,family="gaussian",data=data,verbose=T,mev=vofd,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior1)
#prior2 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=1,alpha.mu=0,alpha.V=1000),G2=list(V=1,nu=1,alpha.mu=0,alpha.V=1000))) # parameter expanded prior (close to non-informative)
#m0.0 <- MCMCglmm(d~1,random=~Study_ID+Strain,family="gaussian",data=data,verbose=T,mev=vofd,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior2)
##test runs - with VCV matrix
#prior3 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=.002),G2=list(V=1,nu=.002),G3=list(V=1,fix=1))) #inverse-Gamma prior with AnivG
#m0.0 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior3)
#m0.0 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
#prior4 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=1,alpha.mu=0,alpha.V=1000),G2=list(V=1,nu=1,alpha.mu=0,alpha.V=1000),G3=list(V=1,fix=1))) #parameter expanded prior with AnivG
#m0.0 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior4)
#summary(m0.0)
#plot(m0.0)


##long runs
prior3 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=.002),G2=list(V=1,nu=.002),G3=list(V=1,fix=1))) #inverse-Gamma prior with AnivG
model_null_BW_full_1 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_null_BW_full_2 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_null_BW_full_3 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
save(model_null_BW_full_1,model_null_BW_full_2,model_null_BW_full_3,file="model_null_BW_full.RData") 
```


Get results.
```{r null model BW full data results, echo=FALSE, eval=TRUE, include=FALSE}
load("model_null_BW_full.RData")
m1 <- model_null_BW_full_1
m2 <- model_null_BW_full_2
m3 <- model_null_BW_full_3

#check model convergence
gelman.diag(list(m1$Sol[,1],m2$Sol[,1],m3$Sol[,1])) #The shrink factors should be below 1.05
gelman.diag(list(m1$VCV[,c(1,2)],m2$VCV[,c(1,2)],m3$VCV[,c(1,2)]))
gelman.diag(list(m1$Deviance,m2$Deviance,m3$Deviance))
#check chain autocorrelation
autocorr(m1$Sol[,c(4)])
autocorr(m1$VCV[,c(1:2)])
autocorr(m2$Sol[,c(4)])
autocorr(m2$VCV[,c(1:2)])
autocorr(m3$Sol[,c(4)])
autocorr(m3$VCV[,c(1:2)])
#extract and summarise DIC
print(c(m1$DIC,m2$DIC,m3$DIC))
mean(c(m1$DIC, m2$DIC, m3$DIC)) 
range(c(m1$DIC, m2$DIC, m3$DIC))  

chosen <- m2

plot(chosen)
summary(chosen)

### heterogeneity and variances
WI <- na.omit(1/data$Bodyweight_Hd_Var_adj) 
s2I <- sum(WI*(length(WI)-1))/(sum(WI)^2-sum(WI^2)) # typical sampling (measurement) error variance (sigma2m)
total_var <- chosen$VCV[,"Study_ID"]+chosen$VCV[,"Strain"]+chosen$VCV[,"units"]+s2I # total variance (sigma2t)
total_het <- (total_var-s2I)/total_var # total heterogeneity I2
#for pasting into Excel table
Study_ID <- round(c(summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Study_ID"]/total_var)*100),1)
Strain <- round(c(summary(chosen$VCV[,"Strain"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Strain"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Strain"]/total_var)*100),1)
units <- round(c(summary(chosen$VCV[,"units"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"units"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"units"]/total_var)*100),1)
total <- round(c(summary(total_het)$statistics[1]*100,summary(total_het)$statistics[2]*100,posterior.mode(total_het)*100),1)
res_df <- t(data.frame(Study_ID=Study_ID,Strain=Strain,units=units,total=total))
# version with mean and range for DIC
res_df<-format(res_df, nsmall = 2)
DICs <- c(m1$DIC, m2$DIC, m3$DIC)
DICmean <- format(round(mean(DICs),2), nsmall = 2)
DICrange <- paste0(format(round(range(DICs)[1],2), nsmall = 2)," - ",format(round(range(DICs)[2],2), nsmall = 2))
res_df <- t(c(paste0(DICmean, "(", DICrange, ")"),
            paste0(res_df[1,1],"(",res_df[1,2],")[",res_df[1,3],"]"),
            paste0(res_df[2,1],"(",res_df[2,2],")[",res_df[2,3],"]"),
            paste0(res_df[3,1],"(",res_df[3,2],")[",res_df[3,3],"]"),
            paste0(res_df[4,1],"(",res_df[4,2],")[",res_df[4,3],"]")))
colnames(res_df) <- c("DIC (DIC range)","I2study","I2strain","I2residual","I2total")
rownames(res_df) <- "mean(SD)[mode]"
write.csv(res_df,"results_table_model_null_BW_full.csv")

### fixed effects (overall intercept)
interc <- c(posterior.mode(chosen$Sol[,1]),summary(chosen$Sol[,1])$statistics[1],summary(chosen$Sol)$statistics[2],HPDinterval(chosen$Sol[,1])[1],HPDinterval(chosen$Sol[,1])[2])
interc <- as.data.frame(t(interc))
rownames(interc) <- c("intercept")
write.table(t(c("Fixed effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_null_BW_full.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(round(interc,3),"results_table_model_null_BW_full.csv", sep=",", col.names = FALSE, append = TRUE)

### random effects
Mode <- posterior.mode(chosen$VCV)
Mean <- summary(chosen$VCV)$statistics[,1]
SD <- summary(chosen$VCV)$statistics[,2]
Lower <- HPDinterval(chosen$VCV)[,1]
Upper <- HPDinterval(chosen$VCV)[,2]
res_df <- data.frame(Mode=Mode,Mean=Mean,SD=SD,Lower=Lower,Upper=Upper)
res_df <- res_df[-(dim(res_df)[1]-1),]
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Study_ID","Strain","residuals")
write.table(t(c("Random effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_null_BW_full.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_null_BW_full.csv", sep=",", col.names = FALSE, append = TRUE)
```

Table.
```{r null model BW full data table, eval=TRUE, echo=FALSE, include=TRUE, message=FALSE, results='asis'}
table <- read.table("results_table_model_null_BW_full.csv", sep=",")
#table
kable(table, digits = 3)
```


# BW - Strain model for the full data set.

Run models.
```{r strain model BW full data, echo=FALSE, eval=FALSE, include=FALSE}
prior3s <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=.002),G3=list(V=1,fix=1))) #inverse-Gamma prior with AnivG
#test run
#m0.0<-MCMCglmm(d~Strain-1,random=~Study_ID+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior3s)
#summary(m0.0)
#long runs
model_strain_BW_full_1 <- MCMCglmm(d~Strain-1,random=~Study_ID+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3s)
model_strain_BW_full_2 <- MCMCglmm(d~Strain-1,random=~Study_ID+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3s)
model_strain_BW_full_3 <- MCMCglmm(d~Strain-1,random=~Study_ID+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3s)
save(model_strain_BW_full_1,model_strain_BW_full_2,model_strain_BW_full_3,file="model_strain_BW_full.RData") 
```

Get results.
```{r strain model BW full data results, echo=FALSE, eval=TRUE, include=FALSE}
load("model_strain_BW_full.RData")
m1 <- model_strain_BW_full_1
m2 <- model_strain_BW_full_2
m3 <- model_strain_BW_full_3

#check model convergence
gelman.diag(list(m1$Sol[,1],m2$Sol[,1],m3$Sol[,1])) #The shrink factors should be below 1.05
gelman.diag(list(m1$VCV[,c(1,3)],m2$VCV[,c(1,3)],m3$VCV[,c(1,3)])) 
gelman.diag(list(m1$Deviance,m2$Deviance,m3$Deviance))
#check chain autocorrelation
autocorr(m1$Sol[,c(2)])
autocorr(m1$VCV[,c(1)])
autocorr(m2$Sol[,c(2)])
autocorr(m2$VCV[,c(1)])
autocorr(m3$Sol[,c(2)])
autocorr(m3$VCV[,c(1)])
#extract and summarise DIC
print(c(m1$DIC,m2$DIC,m3$DIC))
mean(c(m1$DIC, m2$DIC, m3$DIC)) 
range(c(m1$DIC, m2$DIC, m3$DIC))  

chosen <- m3

plot(chosen)
summary(chosen)

### heterogeneity and variances
WI <- na.omit(1/data$Bodyweight_Hd_Var_adj) 
s2I <- sum(WI*(length(WI)-1))/(sum(WI)^2-sum(WI^2)) # typical sampling (measurement) error variance (sigma2m)
total_var <- chosen$VCV[,"Study_ID"]+chosen$VCV[,"units"]+s2I # total variance (sigma2t)
total_het <- (total_var-s2I)/total_var # total heterogeneity I2
#for pasting into Excel table
Study_ID <- round(c(summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Study_ID"]/total_var)*100),1)
units <- round(c(summary(chosen$VCV[,"units"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"units"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"units"]/total_var)*100),1)
total <- round(c(summary(total_het)$statistics[1]*100,summary(total_het)$statistics[2]*100,posterior.mode(total_het)*100),1)
res_df <- t(data.frame(Study_ID=Study_ID,units=units,total=total))
# version with mean and range for DIC
res_df <- format(res_df, nsmall = 2)
DICs <- c(m1$DIC, m2$DIC, m3$DIC)
DICmean <- format(round(mean(DICs),2), nsmall = 2)
DICrange <- paste0(format(round(range(DICs)[1],2), nsmall = 2)," - ",format(round(range(DICs)[2],2), nsmall = 2))
res_df <- t(c(paste0(DICmean, "(", DICrange, ")"),
            paste0(res_df[1,1],"(",res_df[1,2],")[",res_df[1,3],"]"),
            paste0(res_df[2,1],"(",res_df[2,2],")[",res_df[2,3],"]"),
            paste0(res_df[3,1],"(",res_df[3,2],")[",res_df[3,3],"]"), " "))
colnames(res_df) <- c("DIC (DIC range)","I2study","I2residual","I2total", " ")
rownames(res_df) <- "mean(SD)[mode]"
write.csv(res_df,"results_table_model_strain_BW_full.csv")

### fixed effects (8 strains)
#posterior.mode(chosen$Sol)[1:8]  
#summary(chosen$Sol[,1:8])$statistics[,1]   
#HPDinterval(chosen$Sol[,1:8])
mod <- posterior.mode(chosen$Sol)[1:8]
av <- summary(chosen$Sol[,1:8])$statistics[,1]
sd <- summary(chosen$Sol[,1:8])$statistics[,2]
HPDlo <- HPDinterval(chosen$Sol[,1:8])[,1]
HPDhi <- HPDinterval(chosen$Sol[,1:8])[,2]
res_df <- data.frame(Mode=mod,Mean=av,SD=sd,Lower=HPDlo,Upper=HPDhi)
res_df <- res_df[c(7,8,5,1,2,4,3,6),] #reorder strains
res_df <- round(res_df,3)
rownames(res_df) <- c("rat Sprague-Dawley","rat Wistar","rat Long-Evans","mouse C57BL/6","mouse C57BL/6J","mouse ICR","mouse FVB","mouse NMRI" )
write.table(t(c("Fixed effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_strain_BW_full.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_strain_BW_full.csv", sep=",", col.names = FALSE, append = TRUE)

# random effects
#posterior.mode(chosen$VCV) #mode
#summary(chosen$VCV) #mean, SD
#HPDinterval(chosen$VCV) #HPD interval
Mode <- posterior.mode(chosen$VCV)
Mean <- summary(chosen$VCV)$statistics[,1]
SD <- summary(chosen$VCV)$statistics[,2]
Lower <- HPDinterval(chosen$VCV)[,1]
Upper <- HPDinterval(chosen$VCV)[,2]
res_df <- data.frame(Mode=Mode,Mean=Mean,SD=SD,Lower=Lower,Upper=Upper)
res_df <- res_df[-(dim(res_df)[1]-1),]
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Study_ID","residuals")
write.table(t(c("Random effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_strain_BW_full.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_strain_BW_full.csv", sep=",", col.names = FALSE, append = TRUE)
```

Table.
```{r strain model BW full data table, eval=TRUE, echo=FALSE, include=TRUE, message=FALSE, results='asis'}
table <- read.table("results_table_model_strain_BW_full.csv", sep=",")
#table
kable(table, digits = 3)
```

# BW - full1 model for the full data set (with diet stat and end dates)

Run models.
```{r full1 model BW full data, echo=FALSE, eval=FALSE, include=FALSE}
prior3 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=.002),G2=list(V=1,nu=.002),G3=list(V=1,fix=1))) #inverse-Gamma prior with AnivG

#test run
#m0.0 <- MCMCglmm(d~factor(Offspr_sex)+factor(Dam_choice_diet)+Z_Dam_diet_start+Z_Dam_diet_end+Z_Offspr_diet_E+Z_Offspr_diet_PNP_kcal+Z_TBodyweight_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior3)
#summary(m0.0)

#long runs
model_full1_BW_full_1 <- MCMCglmm(d~factor(Offspr_sex)+factor(Dam_choice_diet)+Z_Dam_diet_start+Z_Dam_diet_end+Z_Offspr_diet_E+Z_Offspr_diet_PNP_kcal+Z_TBodyweight_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_full1_BW_full_2 <- MCMCglmm(d~factor(Offspr_sex)+factor(Dam_choice_diet)+Z_Dam_diet_start+Z_Dam_diet_end+Z_Offspr_diet_E+Z_Offspr_diet_PNP_kcal+Z_TBodyweight_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_full1_BW_full_3 <- MCMCglmm(d~factor(Offspr_sex)+factor(Dam_choice_diet)+Z_Dam_diet_start+Z_Dam_diet_end+Z_Offspr_diet_E+Z_Offspr_diet_PNP_kcal+Z_TBodyweight_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
save(model_full1_BW_full_1,model_full1_BW_full_2,model_full1_BW_full_3,file="model_full1_BW_full.RData") 
```

Get results.
```{r full1 model BW full data results, echo=FALSE, eval=TRUE, include=FALSE}
load("model_full1_BW_full.RData")
m1 <- model_full1_BW_full_1
m2 <- model_full1_BW_full_2
m3 <- model_full1_BW_full_3

gelman.diag(list(m1$Sol[,1],m2$Sol[,1],m3$Sol[,1])) #The shrink factors should be below 1.05
gelman.diag(list(m1$VCV[,c(1,2)],m2$VCV[,c(1,2)],m3$VCV[,c(1,2)]))
gelman.diag(list(m1$Deviance,m2$Deviance,m3$Deviance))
#check chain autocorrelation
autocorr(m1$Sol[,c(4)])
autocorr(m1$VCV[,c(1:2)])
autocorr(m2$Sol[,c(4)])
autocorr(m2$VCV[,c(1:2)])
autocorr(m3$Sol[,c(4)])
autocorr(m3$VCV[,c(1:2)])
#extract and summarise DIC
print(c(m1$DIC,m2$DIC,m3$DIC))
mean(c(m1$DIC, m2$DIC, m3$DIC)) 
range(c(m1$DIC, m2$DIC, m3$DIC))  

chosen <- m1

plot(chosen)
summary(chosen)

### heterogeneity and variances
WI <- na.omit(1/data$Bodyweight_Hd_Var_adj) 
s2I <- sum(WI*(length(WI)-1))/(sum(WI)^2-sum(WI^2)) # typical sampling (measurement) error variance (sigma2m)
total_var <- chosen$VCV[,"Study_ID"]+chosen$VCV[,"Strain"]+chosen$VCV[,"units"]+s2I # total variance (sigma2t)
total_het <- (total_var-s2I)/total_var # total heterogeneity I2
#for pasting into Excel table
Study_ID <- round(c(summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Study_ID"]/total_var)*100),1)
Strain <- round(c(summary(chosen$VCV[,"Strain"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Strain"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Strain"]/total_var)*100),1)
units <- round(c(summary(chosen$VCV[,"units"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"units"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"units"]/total_var)*100),1)
total <- round(c(summary(total_het)$statistics[1]*100,summary(total_het)$statistics[2]*100,posterior.mode(total_het)*100),1)
res_df <- t(data.frame(Study_ID=Study_ID,Strain=Strain,units=units,total=total))
# version with mean and range for DIC
res_df <- format(res_df, nsmall = 2)
DICs <- c(m1$DIC, m2$DIC, m3$DIC)
DICmean <- format(round(mean(DICs),2), nsmall = 2)
DICrange <- paste0(format(round(range(DICs)[1],2), nsmall = 2)," - ",format(round(range(DICs)[2],2), nsmall = 2))
res_df <- t(c(paste0(DICmean, "(", DICrange, ")"),
            paste0(res_df[1,1],"(",res_df[1,2],")[",res_df[1,3],"]"),
            paste0(res_df[2,1],"(",res_df[2,2],")[",res_df[2,3],"]"),
            paste0(res_df[3,1],"(",res_df[3,2],")[",res_df[3,3],"]"),
            paste0(res_df[4,1],"(",res_df[4,2],")[",res_df[4,3],"]")))
colnames(res_df) <- c("DIC (DIC range)","I2study","I2strain","I2residual","I2total")
rownames(res_df) <- "mean(SD)[mode]"
write.csv(res_df,"results_table_model_full1_BW_full.csv")

### fixed effects (moderators)
#posterior.mode(chosen$Sol)[1:9]  
#summary(chosen$Sol[,1:9])$statistics[,1]   
#HPDinterval(chosen$Sol[,1:9])
mod <- posterior.mode(chosen$Sol)[1:9]
av <- summary(chosen$Sol[,1:9])$statistics[,1]
sd <- summary(chosen$Sol[,1:9])$statistics[,2]
HPDlo <- HPDinterval(chosen$Sol[,1:9])[,1]
HPDhi <- HPDinterval(chosen$Sol[,1:9])[,2]
res_df <- data.frame(Mode=mod,Mean=av,SD=sd,Lower=HPDlo,Upper=HPDhi)
res_df <- res_df[c(1,3,2,4,5,6,7,8,9),] #reorder moderators
#res_df <- res_df[-(dim(res_df)[1]-1),]
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Offspr. female (interc.)","Offspr. male (interc.)","Offspr. both sex (interc.)","Choice-chow dam diet (diff.)","Dam diet start time","Dam diet end time","Offspr. diet E","Offspr diet P:NP","Offspr. age" )
write.table(t(c("Fixed effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_full1_BW_full.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_full1_BW_full.csv", sep=",", col.names = FALSE, append = TRUE)

### random effects
Mode <- posterior.mode(chosen$VCV)
Mean <- summary(chosen$VCV)$statistics[,1]
SD <- summary(chosen$VCV)$statistics[,2]
Lower <- HPDinterval(chosen$VCV)[,1]
Upper <- HPDinterval(chosen$VCV)[,2]
res_df <- data.frame(Mode=Mode,Mean=Mean,SD=SD,Lower=Lower,Upper=Upper)
res_df <- res_df[-3,]
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Study_ID","Strain","residuals")
write.table(t(c("Random effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_full1_BW_full.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_full1_BW_full.csv", sep=",", col.names = FALSE, append = TRUE)
```

Table.
```{r full1 model BW full data table, eval=TRUE, echo=FALSE, include=TRUE, message=FALSE, results='asis'}
table <- read.table("results_table_model_full1_BW_full.csv", sep=",")
#table
kable(table, digits = 3)
```

# BW - full2 model for the full data set (timing of the diet as categorical variable: lactation included or not)

Run models.
```{r full2 model BW full data, echo=FALSE, eval=FALSE, include=FALSE}
prior3 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=.002),G2=list(V=1,nu=.002),G3=list(V=1,fix=1))) #inverse-Gamma prior with AnivG

#test run
#m0.0 <- MCMCglmm(d~factor(Offspr_sex)+factor(Dam_choice_diet)+factor(Dam_diet_lactation_incl)+Z_Offspr_diet_E+Z_Offspr_diet_PNP_kcal+Z_TBodyweight_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior3)
#summary(m0.0)

#long runs
model_full2_BW_full_1 <- MCMCglmm(d~factor(Offspr_sex)+factor(Dam_choice_diet)+factor(Dam_diet_lactation_incl)+Z_Offspr_diet_E+Z_Offspr_diet_PNP_kcal+Z_TBodyweight_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_full2_BW_full_2 <- MCMCglmm(d~factor(Offspr_sex)+factor(Dam_choice_diet)+factor(Dam_diet_lactation_incl)+Z_Offspr_diet_E+Z_Offspr_diet_PNP_kcal+Z_TBodyweight_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_full2_BW_full_3 <- MCMCglmm(d~factor(Offspr_sex)+factor(Dam_choice_diet)+factor(Dam_diet_lactation_incl)+Z_Offspr_diet_E+Z_Offspr_diet_PNP_kcal+Z_TBodyweight_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)

save(model_full2_BW_full_1,model_full2_BW_full_2,model_full2_BW_full_3,file="model_full2_BW_full.RData") 
```

Get results.
```{r full2 model BW full data results, echo=FALSE, eval=TRUE, include=FALSE}
load("model_full2_BW_full.RData")
m1 <- model_full2_BW_full_1
m2 <- model_full2_BW_full_2
m3 <- model_full2_BW_full_3

gelman.diag(list(m1$Sol[,1],m2$Sol[,1],m3$Sol[,1])) #The shrink factors should be below 1.05
gelman.diag(list(m1$VCV[,c(1,2)],m2$VCV[,c(1,2)],m3$VCV[,c(1,2)]))
gelman.diag(list(m1$Deviance,m2$Deviance,m3$Deviance))
#check chain autocorrelation
autocorr(m1$Sol[,c(4)])
autocorr(m1$VCV[,c(1:2)])
autocorr(m2$Sol[,c(4)])
autocorr(m2$VCV[,c(1:2)])
autocorr(m3$Sol[,c(4)])
autocorr(m3$VCV[,c(1:2)])
#extract and summarise DIC
print(c(m1$DIC,m2$DIC,m3$DIC))
mean(c(m1$DIC, m2$DIC, m3$DIC)) 
range(c(m1$DIC, m2$DIC, m3$DIC))  

chosen <- m3

plot(chosen)
summary(chosen)

### heterogeneity and variances
WI <- na.omit(1/data$Bodyweight_Hd_Var_adj) 
s2I <- sum(WI*(length(WI)-1))/(sum(WI)^2-sum(WI^2)) # typical sampling (measurement) error variance (sigma2m)
total_var <- chosen$VCV[,"Study_ID"]+chosen$VCV[,"Strain"]+chosen$VCV[,"units"]+s2I # total variance (sigma2t)
total_het <- (total_var-s2I)/total_var # total heterogeneity I2
#for pasting into Excel table
Study_ID <- round(c(summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Study_ID"]/total_var)*100),1)
Strain <- round(c(summary(chosen$VCV[,"Strain"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Strain"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Strain"]/total_var)*100),1)
units <- round(c(summary(chosen$VCV[,"units"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"units"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"units"]/total_var)*100),1)
total <- round(c(summary(total_het)$statistics[1]*100,summary(total_het)$statistics[2]*100,posterior.mode(total_het)*100),1)
res_df <- t(data.frame(Study_ID=Study_ID,Strain=Strain,units=units,total=total))
# version with mean and range for DIC
res_df <- format(res_df, nsmall = 2)
DICs <- c(m1$DIC, m2$DIC, m3$DIC)
DICmean <- format(round(mean(DICs),2), nsmall = 2)
DICrange <- paste0(format(round(range(DICs)[1],2), nsmall = 2)," - ",format(round(range(DICs)[2],2), nsmall = 2))
res_df <- t(c(paste0(DICmean, "(", DICrange, ")"),
            paste0(res_df[1,1],"(",res_df[1,2],")[",res_df[1,3],"]"),
            paste0(res_df[2,1],"(",res_df[2,2],")[",res_df[2,3],"]"),
            paste0(res_df[3,1],"(",res_df[3,2],")[",res_df[3,3],"]"),
            paste0(res_df[4,1],"(",res_df[4,2],")[",res_df[4,3],"]")))
colnames(res_df) <- c("DIC (DIC range)","I2study","I2strain","I2residual","I2total")
rownames(res_df) <- "mean(SD)[mode]"
write.csv(res_df,"results_table_model_full2_BW_full.csv")

### fixed effects (moderators)
#posterior.mode(chosen$Sol)[1:8]  
#summary(chosen$Sol[,1:8])$statistics[,1]   
#HPDinterval(chosen$Sol[,1:8])
mod <- posterior.mode(chosen$Sol)[1:8]
av <- summary(chosen$Sol[,1:8])$statistics[,1]
sd <- summary(chosen$Sol[,1:8])$statistics[,2]
HPDlo <- HPDinterval(chosen$Sol[,1:8])[,1]
HPDhi <- HPDinterval(chosen$Sol[,1:8])[,2]
res_df <- data.frame(Mode=mod,Mean=av,SD=sd,Lower=HPDlo,Upper=HPDhi)
res_df <- res_df[c(1,3,2,4:8),] #reorder moderators
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Offspr. female (interc.)","Offspr. male (interc.)","Offspr. both sex (interc.)","Choice-chow dam diet (diff.)","Dam diet during lactation (diff.)","Offspr. diet E","Offspr diet P:NP","Offspr. age" )
write.table(t(c("Fixed effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_full2_BW_full.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_full2_BW_full.csv", sep=",", col.names = FALSE, append = TRUE)

### random effects
Mode <- posterior.mode(chosen$VCV)
Mean <- summary(chosen$VCV)$statistics[,1]
SD <- summary(chosen$VCV)$statistics[,2]
Lower <- HPDinterval(chosen$VCV)[,1]
Upper <- HPDinterval(chosen$VCV)[,2]
res_df <- data.frame(Mode=Mode,Mean=Mean,SD=SD,Lower=Lower,Upper=Upper)
res_df <- res_df[-3,]
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Study_ID","Strain","residuals")
write.table(t(c("Random effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_full2_BW_full.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_full2_BW_full.csv", sep=",", col.names = FALSE, append = TRUE)
```

Table.
```{r full2 model BW full data table, eval=TRUE, echo=FALSE, include=TRUE, message=FALSE, results='asis'}
table <- read.table("results_table_model_full2_BW_full.csv", sep=",")
#table
kable(table, digits = 3)
```


# BW - Null model for the chow data subset.

Define chow data subset variables.
```{r BW chow data, echo=FALSE, eval=TRUE, include=FALSE}
d <- data_NC$Bodyweight_Hd
vofd <- data_NC$Bodyweight_Hd_Var_adj
m_NC <- Bodyweight_matrix_NC
AinvG_NC <- solve(m_NC)
AnivG_NC <- as(AinvG_NC,"dgCMatrix")
```

Run models.
```{r null model BW chow data, echo=FALSE, eval=FALSE, include=FALSE}
#prior3 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=.002),G2=list(V=1,nu=.002),G3=list(V=1,fix=1))) #inverse-Gamma prior with AnivG
##test runs - with VCV matrix
#m0.0 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior3)
#m0.0 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
#prior4 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=1,alpha.mu=0,alpha.V=1000),G2=list(V=1,nu=1,alpha.mu=0,alpha.V=1000),G3=list(V=1,fix=1))) #parameter expanded prior with AnivG
#m0.0 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior4)
#summary(m0.0)
#plot(m0.0)

##long runs
prior3 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=.002),G2=list(V=1,nu=.002),G3=list(V=1,fix=1))) #inverse-Gamma prior with AnivG
model_null_BW_chow_1 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_null_BW_chow_2 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_null_BW_chow_3 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
save(model_null_BW_chow_1,model_null_BW_chow_2,model_null_BW_chow_3,file="model_null_BW_chow.RData") 
```

Get results.
```{r null model BW chow data results, echo=FALSE, eval=TRUE, include=FALSE}
load("model_null_BW_chow.RData")
m1 <- model_null_BW_chow_1
m2 <- model_null_BW_chow_2
m3 <- model_null_BW_chow_3

#check model convergence
gelman.diag(list(m1$Sol[,1],m2$Sol[,1],m3$Sol[,1])) #The shrink factors should be below 1.05
gelman.diag(list(m1$VCV[,c(1,2)],m2$VCV[,c(1,2)],m3$VCV[,c(1,2)]))
gelman.diag(list(m1$Deviance,m2$Deviance,m3$Deviance))
#check chain autocorrelation
autocorr(m1$Sol[,c(4)])
autocorr(m1$VCV[,c(1:2)])
autocorr(m2$Sol[,c(4)])
autocorr(m2$VCV[,c(1:2)])
autocorr(m3$Sol[,c(4)])
autocorr(m3$VCV[,c(1:2)])
#extract and summarise DIC
print(c(m1$DIC,m2$DIC,m3$DIC))
mean(c(m1$DIC, m2$DIC, m3$DIC)) 
range(c(m1$DIC, m2$DIC, m3$DIC))  

chosen <- m1

plot(chosen)
summary(chosen)

### heterogeneity and variances
WI <- na.omit(1/data_NC$Bodyweight_Hd_Var_adj) 
s2I <- sum(WI*(length(WI)-1))/(sum(WI)^2-sum(WI^2)) # typical sampling (measurement) error variance (sigma2m)
total_var <- chosen$VCV[,"Study_ID"]+chosen$VCV[,"Strain"]+chosen$VCV[,"units"]+s2I # total variance (sigma2t)
total_het <- (total_var-s2I)/total_var # total heterogeneity I2
#for pasting into Excel table
Study_ID <- round(c(summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Study_ID"]/total_var)*100),1)
Strain <- round(c(summary(chosen$VCV[,"Strain"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Strain"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Strain"]/total_var)*100),1)
units <- round(c(summary(chosen$VCV[,"units"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"units"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"units"]/total_var)*100),1)
total <- round(c(summary(total_het)$statistics[1]*100,summary(total_het)$statistics[2]*100,posterior.mode(total_het)*100),1)
res_df <- t(data.frame(Study_ID=Study_ID,Strain=Strain,units=units,total=total))
# version with mean and range for DIC
res_df <- format(res_df, nsmall = 2)
DICs <- c(m1$DIC, m2$DIC, m3$DIC)
DICmean <- format(round(mean(DICs),2), nsmall = 2)
DICrange <- paste0(format(round(range(DICs)[1],2), nsmall = 2)," - ",format(round(range(DICs)[2],2), nsmall = 2))
res_df <- t(c(paste0(DICmean, "(", DICrange, ")"),
            paste0(res_df[1,1],"(",res_df[1,2],")[",res_df[1,3],"]"),
            paste0(res_df[2,1],"(",res_df[2,2],")[",res_df[2,3],"]"),
            paste0(res_df[3,1],"(",res_df[3,2],")[",res_df[3,3],"]"),
            paste0(res_df[4,1],"(",res_df[4,2],")[",res_df[4,3],"]")))
colnames(res_df) <- c("DIC (DIC range)","I2study","I2strain","I2residual","I2total")
rownames(res_df) <- "mean(SD)[mode]"
write.csv(res_df,"results_table_model_null_BW_chow.csv")

### fixed effects (overall intercept)
interc <- c(posterior.mode(chosen$Sol[,1]),summary(chosen$Sol[,1])$statistics[1],summary(chosen$Sol)$statistics[2],HPDinterval(chosen$Sol[,1])[1],HPDinterval(chosen$Sol[,1])[2])
interc <- as.data.frame(t(interc))
rownames(interc) <- c("intercept")
write.table(t(c("Fixed effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_null_BW_chow.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(round(interc,3),"results_table_model_null_BW_chow.csv", sep=",", col.names = FALSE, append = TRUE)

### random effects
Mode <- posterior.mode(chosen$VCV)
Mean <- summary(chosen$VCV)$statistics[,1]
SD <- summary(chosen$VCV)$statistics[,2]
Lower <- HPDinterval(chosen$VCV)[,1]
Upper <- HPDinterval(chosen$VCV)[,2]
res_df <- data.frame(Mode=Mode,Mean=Mean,SD=SD,Lower=Lower,Upper=Upper)
res_df <- res_df[-(dim(res_df)[1]-1),]
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Study_ID","Strain","residuals")
write.table(t(c("Random effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_null_BW_chow.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_null_BW_chow.csv", sep=",", col.names = FALSE, append = TRUE)
```

Table.
```{r null model BW chow data table, eval=TRUE, echo=FALSE, include=TRUE, message=FALSE, results='asis'}
table <- read.table("results_table_model_null_BW_chow.csv", sep=",")
#table
kable(table, digits = 3)
```

# BW - Strain model for the chow data subset.

Run models.
```{r strain model BW chow data, echo=FALSE, eval=FALSE, include=FALSE}
prior3s <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=.002),G3=list(V=1,fix=1))) #inverse-Gamma prior with AnivG

##test runs - with VCV matrix
#m0.0 <- MCMCglmm(d~Strain-1,random=~Study_ID+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior3s)
#prior4 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=1,alpha.mu=0,alpha.V=1000),G2=list(V=1,nu=1,alpha.mu=0,alpha.V=1000),G3=list(V=1,fix=1))) #parameter expanded prior with AnivG
#m0.0 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior4)
#summary(m0.0)

##long runs
model_strain_BW_chow_1 <- MCMCglmm(d~Strain-1,random=~Study_ID+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3s)
model_strain_BW_chow_2 <- MCMCglmm(d~Strain-1,random=~Study_ID+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3s)
model_strain_BW_chow_3 <- MCMCglmm(d~Strain-1,random=~Study_ID+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3s)
save(model_strain_BW_chow_1,model_strain_BW_chow_2,model_strain_BW_chow_3,file="model_strain_BW_chow.RData") 
```

Get results.
```{r strain model BW chow data results, echo=FALSE, eval=TRUE, include=FALSE}
load("model_strain_BW_chow.RData")
m1 <- model_strain_BW_chow_1
m2 <- model_strain_BW_chow_2
m3 <- model_strain_BW_chow_3

#check model convergence
gelman.diag(list(m1$Sol[,1],m2$Sol[,1],m3$Sol[,1])) #The shrink factors should be below 1.05
gelman.diag(list(m1$VCV[,c(1,3)],m2$VCV[,c(1,3)],m3$VCV[,c(1,3)])) 
gelman.diag(list(m1$Deviance,m2$Deviance,m3$Deviance))
#check chain autocorrelation
autocorr(m1$Sol[,c(2)])
autocorr(m1$VCV[,c(1)])
autocorr(m2$Sol[,c(2)])
autocorr(m2$VCV[,c(1)])
autocorr(m3$Sol[,c(2)])
autocorr(m3$VCV[,c(1)])
#extract and summarise DIC
print(c(m1$DIC,m2$DIC,m3$DIC))
mean(c(m1$DIC, m2$DIC, m3$DIC)) 
range(c(m1$DIC, m2$DIC, m3$DIC))  

chosen <- m2

plot(chosen)
summary(chosen)

### heterogeneity and variances
WI <- na.omit(1/data_NC$Bodyweight_Hd_Var_adj) 
s2I <- sum(WI*(length(WI)-1))/(sum(WI)^2-sum(WI^2)) # typical sampling (measurement) error variance (sigma2m)
total_var <- chosen$VCV[,"Study_ID"]+chosen$VCV[,"units"]+s2I # total variance (sigma2t)
total_het <- (total_var-s2I)/total_var # total heterogeneity I2
#for pasting into Excel table
Study_ID <- round(c(summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Study_ID"]/total_var)*100),1)
units <- round(c(summary(chosen$VCV[,"units"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"units"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"units"]/total_var)*100),1)
total <- round(c(summary(total_het)$statistics[1]*100,summary(total_het)$statistics[2]*100,posterior.mode(total_het)*100),1)
res_df <- t(data.frame(Study_ID=Study_ID,units=units,total=total))
# version with mean and range for DIC
res_df <- format(res_df, nsmall = 2)
DICs <- c(m1$DIC, m2$DIC, m3$DIC)
DICmean <- format(round(mean(DICs),2), nsmall = 2)
DICrange <- paste0(format(round(range(DICs)[1],2), nsmall = 2)," - ",format(round(range(DICs)[2],2), nsmall = 2))
res_df <- t(c(paste0(DICmean, "(", DICrange, ")"),
            paste0(res_df[1,1],"(",res_df[1,2],")[",res_df[1,3],"]"),
            paste0(res_df[2,1],"(",res_df[2,2],")[",res_df[2,3],"]"),
            paste0(res_df[3,1],"(",res_df[3,2],")[",res_df[3,3],"]"), " "))
colnames(res_df) <- c("DIC (DIC range)","I2study","I2residual","I2total", " ")
rownames(res_df) <- "mean(SD)[mode]"
write.csv(res_df,"results_table_model_strain_BW_chow.csv")

### fixed effects (8 strains)
#posterior.mode(chosen$Sol)[1:8]  
#summary(chosen$Sol[,1:8])$statistics[,1]   
#HPDinterval(chosen$Sol[,1:8])
mod <- posterior.mode(chosen$Sol)[1:8]
av <- summary(chosen$Sol[,1:8])$statistics[,1]
sd <- summary(chosen$Sol[,1:8])$statistics[,2]
HPDlo <- HPDinterval(chosen$Sol[,1:8])[,1]
HPDhi <- HPDinterval(chosen$Sol[,1:8])[,2]
res_df <- data.frame(Mode=mod,Mean=av,SD=sd,Lower=HPDlo,Upper=HPDhi)
res_df <- res_df[c(7,8,5,1,2,4,3,6),] #reorder strains
res_df <- round(res_df,3)
rownames(res_df) <- c("rat Sprague-Dawley","rat Wistar","rat Long-Evans","mouse C57BL/6","mouse C57BL/6J","mouse ICR","mouse FVB","mouse NMRI" )
write.table(t(c("Fixed effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_strain_BW_chow.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_strain_BW_chow.csv", sep=",", col.names = FALSE, append = TRUE)

# random effects
#posterior.mode(chosen$VCV) #mode
#summary(chosen$VCV) #mean, SD
#HPDinterval(chosen$VCV) #HPD interval
Mode <- posterior.mode(chosen$VCV)
Mean <- summary(chosen$VCV)$statistics[,1]
SD <- summary(chosen$VCV)$statistics[,2]
Lower <- HPDinterval(chosen$VCV)[,1]
Upper <- HPDinterval(chosen$VCV)[,2]
res_df <- data.frame(Mode=Mode,Mean=Mean,SD=SD,Lower=Lower,Upper=Upper)
res_df <- res_df[-(dim(res_df)[1]-1),]
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Study_ID","residuals")
write.table(t(c("Random effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_strain_BW_chow.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_strain_BW_chow.csv", sep=",", col.names = FALSE, append = TRUE)
```

Table.
```{r strain model BW chow data table, eval=TRUE, echo=FALSE, include=TRUE, message=FALSE, results='asis'}
table <- read.table("results_table_model_strain_BW_chow.csv", sep=",")
#table
kable(table, digits = 3)
```

# BW - full1 model for the chow data subset (with diet stat and end dates)

Run models.
```{r full1 model BW chow data, echo=FALSE, eval=FALSE, include=FALSE}
prior3 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=.002),G2=list(V=1,nu=.002),G3=list(V=1,fix=1))) #inverse-Gamma prior with AnivG

#test run
#m0.0 <- MCMCglmm(d~factor(Offspr_sex)+Z_Dam_diet_start+Z_Dam_diet_end+Z_Dam_diet_exp_E+Z_Dam_diet_exp_PNP_kcal+Z_TBodyweight_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior3)
#summary(m0.0)

#long runs
model_full1_BW_chow_1 <- MCMCglmm(d~factor(Offspr_sex)+Z_Dam_diet_start+Z_Dam_diet_end+Z_Dam_diet_exp_E+Z_Dam_diet_exp_PNP_kcal+Z_TBodyweight_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_full1_BW_chow_2 <- MCMCglmm(d~factor(Offspr_sex)+Z_Dam_diet_start+Z_Dam_diet_end+Z_Dam_diet_exp_E+Z_Dam_diet_exp_PNP_kcal+Z_TBodyweight_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_full1_BW_chow_3 <- MCMCglmm(d~factor(Offspr_sex)+Z_Dam_diet_start+Z_Dam_diet_end+Z_Dam_diet_exp_E+Z_Dam_diet_exp_PNP_kcal+Z_TBodyweight_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
save(model_full1_BW_chow_1,model_full1_BW_chow_2,model_full1_BW_chow_3,file="model_full1_BW_chow.RData") 
```

Get results.
```{r full1 model BW chow data results, echo=FALSE, eval=TRUE, include=FALSE}
load("model_full1_BW_chow.RData")
m1 <- model_full1_BW_chow_1
m2 <- model_full1_BW_chow_2
m3 <- model_full1_BW_chow_3

gelman.diag(list(m1$Sol[,1],m2$Sol[,1],m3$Sol[,1])) #The shrink factors should be below 1.05
gelman.diag(list(m1$VCV[,c(1,2)],m2$VCV[,c(1,2)],m3$VCV[,c(1,2)]))
gelman.diag(list(m1$Deviance,m2$Deviance,m3$Deviance))
#check chain autocorrelation
autocorr(m1$Sol[,c(4)])
autocorr(m1$VCV[,c(1:2)])
autocorr(m2$Sol[,c(4)])
autocorr(m2$VCV[,c(1:2)])
autocorr(m3$Sol[,c(4)])
autocorr(m3$VCV[,c(1:2)])
#extract and summarise DIC
print(c(m1$DIC,m2$DIC,m3$DIC))
mean(c(m1$DIC, m2$DIC, m3$DIC)) 
range(c(m1$DIC, m2$DIC, m3$DIC))  

chosen <- m2

plot(chosen)
summary(chosen)

### heterogeneity and variances
WI <- na.omit(1/data_NC$Bodyweight_Hd_Var_adj) 
s2I <- sum(WI*(length(WI)-1))/(sum(WI)^2-sum(WI^2)) # typical sampling (measurement) error variance (sigma2m)
total_var <- chosen$VCV[,"Study_ID"]+chosen$VCV[,"Strain"]+chosen$VCV[,"units"]+s2I # total variance (sigma2t)
total_het <- (total_var-s2I)/total_var # total heterogeneity I2
#for pasting into Excel table
Study_ID <- round(c(summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Study_ID"]/total_var)*100),1)
Strain <- round(c(summary(chosen$VCV[,"Strain"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Strain"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Strain"]/total_var)*100),1)
units <- round(c(summary(chosen$VCV[,"units"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"units"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"units"]/total_var)*100),1)
total <- round(c(summary(total_het)$statistics[1]*100,summary(total_het)$statistics[2]*100,posterior.mode(total_het)*100),1)
res_df <- t(data.frame(Study_ID=Study_ID,Strain=Strain,units=units,total=total))
# version with mean and range for DIC
res_df <- format(res_df, nsmall = 2)
DICs <- c(m1$DIC, m2$DIC, m3$DIC)
DICmean <- format(round(mean(DICs),2), nsmall = 2)
DICrange <- paste0(format(round(range(DICs)[1],2), nsmall = 2)," - ",format(round(range(DICs)[2],2), nsmall = 2))
res_df <- t(c(paste0(DICmean, "(", DICrange, ")"),
            paste0(res_df[1,1],"(",res_df[1,2],")[",res_df[1,3],"]"),
            paste0(res_df[2,1],"(",res_df[2,2],")[",res_df[2,3],"]"),
            paste0(res_df[3,1],"(",res_df[3,2],")[",res_df[3,3],"]"),
            paste0(res_df[4,1],"(",res_df[4,2],")[",res_df[4,3],"]")))
colnames(res_df) <- c("DIC (DIC range)","I2study","I2strain","I2residual","I2total")
rownames(res_df) <- "mean(SD)[mode]"
write.csv(res_df,"results_table_model_full1_BW_chow.csv")

### fixed effects (moderators)
#posterior.mode(chosen$Sol)[1:7]  
#summary(chosen$Sol[,1:7])$statistics[,1]   
#HPDinterval(chosen$Sol[,1:7])
mod <- posterior.mode(chosen$Sol)[1:7]
av <- summary(chosen$Sol[,1:7])$statistics[,1]
sd <- summary(chosen$Sol[,1:7])$statistics[,2]
HPDlo <- HPDinterval(chosen$Sol[,1:7])[,1]
HPDhi <- HPDinterval(chosen$Sol[,1:7])[,2]
res_df <- data.frame(Mode=mod,Mean=av,SD=sd,Lower=HPDlo,Upper=HPDhi)
#res_df <- res_df[-(dim(res_df)[1]-1),]
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Offspr. female (interc.)","Offspr. male (interc.)","Dam diet start time","Dam diet end time","Dam diet E","Dam diet P:NP","Offspr. age" )
write.table(t(c("Fixed effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_full1_BW_chow.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_full1_BW_chow.csv", sep=",", col.names = FALSE, append = TRUE)

### random effects
Mode <- posterior.mode(chosen$VCV)
Mean <- summary(chosen$VCV)$statistics[,1]
SD <- summary(chosen$VCV)$statistics[,2]
Lower <- HPDinterval(chosen$VCV)[,1]
Upper <- HPDinterval(chosen$VCV)[,2]
res_df <- data.frame(Mode=Mode,Mean=Mean,SD=SD,Lower=Lower,Upper=Upper)
res_df <- res_df[-3,]
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Study_ID","Strain","residuals")
write.table(t(c("Random effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_full1_BW_chow.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_full1_BW_chow.csv", sep=",", col.names = FALSE, append = TRUE)
```

Table.
```{r full1 model BW chow data table, eval=TRUE, echo=FALSE, include=TRUE, message=FALSE, results='asis'}
table <- read.table("results_table_model_full1_BW_full.csv", sep=",")
#table
kable(table, digits = 3)
```

# BW - full2 model for the chow data subset (timing of the diet as categorical variable: lactation included or not)

Run models.
```{r full2 model BW chow data, echo=FALSE, eval=FALSE, include=FALSE}
prior3 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=.002),G2=list(V=1,nu=.002),G3=list(V=1,fix=1))) #inverse-Gamma prior with AnivG

#test run
#m0.0 <- MCMCglmm(d~factor(Offspr_sex)+factor(Dam_diet_lactation_incl)+Z_Dam_diet_exp_E+Z_Dam_diet_exp_PNP_kcal+Z_TBodyweight_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=44000,thin=40,burnin=4000,pr=T,prior=prior3)
#summary(m0.0)

#long runs
model_full2_BW_chow_1 <- MCMCglmm(d~factor(Offspr_sex)+factor(Dam_diet_lactation_incl)+Z_Dam_diet_exp_E+Z_Dam_diet_exp_PNP_kcal+Z_TBodyweight_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_full2_BW_chow_2 <- MCMCglmm(d~factor(Offspr_sex)+factor(Dam_diet_lactation_incl)+Z_Dam_diet_exp_E+Z_Dam_diet_exp_PNP_kcal+Z_TBodyweight_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_full2_BW_chow_3 <- MCMCglmm(d~factor(Offspr_sex)+factor(Dam_diet_lactation_incl)+Z_Dam_diet_exp_E+Z_Dam_diet_exp_PNP_kcal+Z_TBodyweight_age_dPC-1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data_NC,ginverse=list(ES_ID=AnivG_NC), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
save(model_full2_BW_chow_1,model_full2_BW_chow_2,model_full2_BW_chow_3,file="model_full2_BW_chow.RData") 
```

Get results.
```{r full2 model BW chow data results, echo=FALSE, eval=TRUE, include=FALSE}
load("model_full2_BW_chow.RData")
m1 <- model_full2_BW_chow_1
m2 <- model_full2_BW_chow_2
m3 <- model_full2_BW_chow_3

gelman.diag(list(m1$Sol[,1],m2$Sol[,1],m3$Sol[,1])) #The shrink factors should be below 1.05
gelman.diag(list(m1$VCV[,c(1,2)],m2$VCV[,c(1,2)],m3$VCV[,c(1,2)]))
gelman.diag(list(m1$Deviance,m2$Deviance,m3$Deviance))
#check chain autocorrelation
autocorr(m1$Sol[,c(4)])
autocorr(m1$VCV[,c(1:2)])
autocorr(m2$Sol[,c(4)])
autocorr(m2$VCV[,c(1:2)])
autocorr(m3$Sol[,c(4)])
autocorr(m3$VCV[,c(1:2)])
#extract and summarise DIC
print(c(m1$DIC,m2$DIC,m3$DIC))
mean(c(m1$DIC, m2$DIC, m3$DIC)) 
range(c(m1$DIC, m2$DIC, m3$DIC))  

chosen <- m3

plot(chosen)
summary(chosen)

### heterogeneity and variances
WI <- na.omit(1/data_NC$Bodyweight_Hd_Var_adj) 
s2I <- sum(WI*(length(WI)-1))/(sum(WI)^2-sum(WI^2)) # typical sampling (measurement) error variance (sigma2m)
total_var <- chosen$VCV[,"Study_ID"]+chosen$VCV[,"Strain"]+chosen$VCV[,"units"]+s2I # total variance (sigma2t)
total_het <- (total_var-s2I)/total_var # total heterogeneity I2
#for pasting into Excel table
Study_ID <- round(c(summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Study_ID"]/total_var)*100),1)
Strain <- round(c(summary(chosen$VCV[,"Strain"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Strain"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Strain"]/total_var)*100),1)
units <- round(c(summary(chosen$VCV[,"units"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"units"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"units"]/total_var)*100),1)
total <- round(c(summary(total_het)$statistics[1]*100,summary(total_het)$statistics[2]*100,posterior.mode(total_het)*100),1)
res_df <- t(data.frame(Study_ID=Study_ID,Strain=Strain,units=units,total=total))
# version with mean and range for DIC
res_df <- format(res_df, nsmall = 2)
DICs <- c(m1$DIC, m2$DIC, m3$DIC)
DICmean <- format(round(mean(DICs),2), nsmall = 2)
DICrange <- paste0(format(round(range(DICs)[1],2), nsmall = 2)," - ",format(round(range(DICs)[2],2), nsmall = 2))
res_df <- t(c(paste0(DICmean, "(", DICrange, ")"),
            paste0(res_df[1,1],"(",res_df[1,2],")[",res_df[1,3],"]"),
            paste0(res_df[2,1],"(",res_df[2,2],")[",res_df[2,3],"]"),
            paste0(res_df[3,1],"(",res_df[3,2],")[",res_df[3,3],"]"),
            paste0(res_df[4,1],"(",res_df[4,2],")[",res_df[4,3],"]")))
colnames(res_df) <- c("DIC (DIC range)","I2study","I2strain","I2residual","I2total")
rownames(res_df) <- "mean(SD)[mode]"
write.csv(res_df,"results_table_model_full2_BW_chow.csv")

### fixed effects (moderators)
#posterior.mode(chosen$Sol)[1:6]  
#summary(chosen$Sol[,1:6])$statistics[,1]   
#HPDinterval(chosen$Sol[,1:6])
mod <- posterior.mode(chosen$Sol)[1:6]
av <- summary(chosen$Sol[,1:6])$statistics[,1]
sd <- summary(chosen$Sol[,1:6])$statistics[,2]
HPDlo <- HPDinterval(chosen$Sol[,1:6])[,1]
HPDhi <- HPDinterval(chosen$Sol[,1:6])[,2]
res_df <- data.frame(Mode=mod,Mean=av,SD=sd,Lower=HPDlo,Upper=HPDhi)
#res_df <- res_df[c(1,3,2,4:6),] #reorder moderators
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Offspr. female (interc.)","Offspr. male (interc.)","Dam diet during lactation (diff.)","Dam diet E","Dam diet P:NP","Offspr. age" )
write.table(t(c("Fixed effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_full2_BW_chow.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_full2_BW_chow.csv", sep=",", col.names = FALSE, append = TRUE)

### random effects
Mode <- posterior.mode(chosen$VCV)
Mean <- summary(chosen$VCV)$statistics[,1]
SD <- summary(chosen$VCV)$statistics[,2]
Lower <- HPDinterval(chosen$VCV)[,1]
Upper <- HPDinterval(chosen$VCV)[,2]
res_df <- data.frame(Mode=Mode,Mean=Mean,SD=SD,Lower=Lower,Upper=Upper)
res_df <- res_df[-3,]
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Study_ID","Strain","residuals")
write.table(t(c("Random effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_full2_BW_chow.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_full2_BW_chow.csv", sep=",", col.names = FALSE, append = TRUE)
```

Table.
```{r full2 model BW chow data table, eval=TRUE, echo=FALSE, include=TRUE, message=FALSE, results='asis'}
table <- read.table("results_table_model_full2_BW_chow.csv", sep=",")
#table
kable(table, digits = 3)
```


COMBINE MODEL AND RESULTS TABLES FOR EACH DATA SET
--------------------------------------------------

```{r load all results tables, eval=TRUE, echo=FALSE, include=TRUE, message=FALSE, results='asis'}
table_null_RI2_full <- read.table("results_table_model_null_RI2_full.csv", sep=",")
table_strain_RI2_full <- read.table("results_table_model_strain_RI2_full.csv", sep=",")
table_full1_RI2_full <- read.table("results_table_model_full1_RI2_full.csv", sep=",")
table_full2_RI2_full <- read.table("results_table_model_full2_RI2_full.csv", sep=",")

table_null_RI2_chow <- read.table("results_table_model_null_RI2_chow.csv", sep=",")
table_strain_RI2_chow <- read.table("results_table_model_strain_RI2_chow.csv", sep=",")
table_full1_RI2_chow <- read.table("results_table_model_full1_RI2_chow.csv", sep=",")
table_full2_RI2_chow <- read.table("results_table_model_full2_RI2_chow.csv", sep=",")

table_null_BW_full <- read.table("results_table_model_null_BW_full.csv", sep=",")
table_strain_BW_full <- read.table("results_table_model_strain_BW_full.csv", sep=",")
table_full1_BW_full <- read.table("results_table_model_full1_BW_full.csv", sep=",")
table_full2_BW_full <- read.table("results_table_model_full2_BW_full.csv", sep=",")

table_null_BW_chow <- read.table("results_table_model_null_BW_chow.csv", sep=",")
table_strain_BW_chow <- read.table("results_table_model_strain_BW_chow.csv", sep=",")
table_full1_BW_chow <- read.table("results_table_model_full1_BW_chow.csv", sep=",")
table_full2_BW_chow <- read.table("results_table_model_full2_BW_chow.csv", sep=",")
```

Test results tables for RI2_full analyses only
```{r test combine results tables, eval=FALSE, echo=FALSE, include=FALSE, message=FALSE, results='asis'}
#options(stringsAsFactors = FALSE) #does not seem to work

#RI2_full stats table
heter_table <- table_null_RI2_full[1:2,2:6]
heter_table <- rbind(heter_table, table_strain_RI2_full[2,2:6])
heter_table <- rbind(heter_table, table_full1_RI2_full[2,2:6])
heter_table <- rbind(heter_table, table_full2_RI2_full[2,2:6])
colnames(heter_table) <- c("DIC","I2study","I2strain","I2residual","I2total")
heter_table <- data.frame(lapply(heter_table, as.character), stringsAsFactors=FALSE)
heter_table[2,5] <- heter_table[2,4]
heter_table[2,4] <- heter_table[2,3]
heter_table[2,3] <- "-"
params_table <- data.frame(Data = c("Data",rep("RI2_full",4)), Model = c("Model","1(null)", "2(strain)", "2(full)", "4(full alt.)"), FixedEffects = c("Fixed Effects","Intercept","Strain","Offspr. sex, Choice dam diet, Dam diet start time, Dam diet end time, Offspr. diet E, Offspr diet P:NP, Offspr. age","Offspr. sex, Choice dam diet, Dam diet during lactation, Offspr. diet E,   Offspr diet P:NP, Offspr. age"), RandomEffects = c("Random Effects","Study, Strain","Strain","Study, Strain","Study, Strain"))
ph_table <- cbind(params_table, heter_table) 

##RI2_full stats table
stats_table <- table_null_RI2_full[3:4,]
stats_table <- rbind(stats_table, table_strain_RI2_full[3:11,])
stats_table <- rbind(stats_table, table_full1_RI2_full[3:12,])
stats_table <- rbind(stats_table, table_full2_RI2_full[3:11,])
stats_table <- rbind(stats_table, table_null_RI2_full[5:8,])
stats_table <- rbind(stats_table, table_strain_RI2_full[12:14,])
stats_table <- rbind(stats_table, table_full1_RI2_full[13:16,])
stats_table <- rbind(stats_table, table_full2_RI2_full[12:15,])
dim(stats_table)
stats_table
stats_table <- cbind(Model = c("1(null)"," ","2(strain)",rep(" ", 8),"2(full)",rep(" ", 9),"4(full alt.)", rep(" ", 8),"1(null)", rep(" ", 3),"2(strain)", rep(" ", 2), "2(full)", rep(" ", 3), "4(full alt.)", rep(" ", 3)), stats_table)
stats_table <- cbind(Data = rep("RI2_full", nrow(stats_table)), stats_table)
stats_table
```

Models tables for all analyses

```{r all combine models tables, eval=TRUE, echo=FALSE, include=TRUE, message=FALSE, results='asis'}
#RI2_full models table
heter_table <- table_null_RI2_full[1:2,2:6]
heter_table <- rbind(heter_table, table_strain_RI2_full[2,2:6])
heter_table <- rbind(heter_table, table_full1_RI2_full[2,2:6])
heter_table <- rbind(heter_table, table_full2_RI2_full[2,2:6])
colnames(heter_table) <- c("DIC","I2study","I2strain","I2residual","I2total")
heter_table <- data.frame(lapply(heter_table, as.character), stringsAsFactors=FALSE)
heter_table[3,5] <- heter_table[3,4]
heter_table[3,4] <- heter_table[3,3]
heter_table[3,3] <- "-"
params_table <- data.frame(Data = c("Data",rep("RI2_full",4)), Model = c("Model","1(null)", "2(strain)", "2(full)", "4(full alt.)"), FixedEffects = c("Fixed Effects","Intercept","Strain","Offspr. sex, Choice dam diet, Dam diet start time, Dam diet end time, Offspr. diet E, Offspr. diet P:NP, Offspr. age","Offspr. sex, Choice dam diet, Dam diet during lactation, Offspr. diet E, Offspr. diet P:NP, Offspr. age"), RandomEffects = c("Random Effects","Study, Strain","Strain","Study, Strain","Study, Strain"))
join_table <- cbind(params_table, heter_table) 
models_table <- join_table

#RI2_chow models table
heter_table <- table_null_RI2_chow[1:2,2:6]
heter_table <- rbind(heter_table, table_strain_RI2_chow[2,2:6])
heter_table <- rbind(heter_table, table_full1_RI2_chow[2,2:6])
heter_table <- rbind(heter_table, table_full2_RI2_chow[2,2:6])
colnames(heter_table) <- c("DIC","I2study","I2strain","I2residual","I2total")
heter_table <- data.frame(lapply(heter_table, as.character), stringsAsFactors=FALSE)
heter_table[3,5] <- heter_table[3,4]
heter_table[3,4] <- heter_table[3,3]
heter_table[3,3] <- "-"
params_table <- data.frame(Data = c("Data",rep("RI2_chow",4)), Model = c("Model","1(null)", "2(strain)", "2(full)", "4(full alt.)"), FixedEffects = c("Fixed Effects","Intercept","Strain","Offspr. sex, Dam diet start time, Dam diet end time, Dam diet E, Dam diet P:NP, Offspr. age","Offspr. sex, Dam diet during lactation, Dam diet E, Dam diet P:NP, Offspr. age"), RandomEffects = c("Random Effects","Study, Strain","Strain","Study, Strain","Study, Strain"))
join_table <- cbind(params_table, heter_table) 
models_table <- rbind(models_table, join_table)

#BW_full models table
heter_table <- table_null_BW_full[1:2,2:6]
heter_table <- rbind(heter_table, table_strain_BW_full[2,2:6])
heter_table <- rbind(heter_table, table_full1_BW_full[2,2:6])
heter_table <- rbind(heter_table, table_full2_BW_full[2,2:6])
colnames(heter_table) <- c("DIC","I2study","I2strain","I2residual","I2total")
heter_table <- data.frame(lapply(heter_table, as.character), stringsAsFactors=FALSE)
heter_table[3,5] <- heter_table[3,4]
heter_table[3,4] <- heter_table[3,3]
heter_table[3,3] <- "-"
params_table <- data.frame(Data = c("Data",rep("BW_full",4)), Model = c("Model","1(null)", "2(strain)", "2(full)", "4(full alt.)"), FixedEffects = c("Fixed Effects","Intercept","Strain","Offspr. sex, Choice dam diet, Dam diet start time, Dam diet end time, Offspr. diet E, Offspr. diet P:NP, Offspr. age","Offspr. sex, Choice dam diet, Dam diet during lactation, Offspr. diet E, Offspr. diet P:NP, Offspr. age"), RandomEffects = c("Random Effects","Study, Strain","Strain","Study, Strain","Study, Strain"))
join_table <- cbind(params_table, heter_table) 
models_table <- rbind(models_table, join_table)

#BW_chow models table
heter_table <- table_null_BW_chow[1:2,2:6]
heter_table <- rbind(heter_table, table_strain_BW_chow[2,2:6])
heter_table <- rbind(heter_table, table_full1_BW_chow[2,2:6])
heter_table <- rbind(heter_table, table_full2_BW_chow[2,2:6])
colnames(heter_table) <- c("DIC","I2study","I2strain","I2residual","I2total")
heter_table <- data.frame(lapply(heter_table, as.character), stringsAsFactors=FALSE)
heter_table[3,5] <- heter_table[3,4]
heter_table[3,4] <- heter_table[3,3]
heter_table[3,3] <- "-"
params_table <- data.frame(Data = c("Data",rep("BW_chow",4)), Model = c("Model","1(null)", "2(strain)", "2(full)", "4(full alt.)"), FixedEffects = c("Fixed Effects","Intercept","Strain","Offspr. sex, Dam diet start time, Dam diet end time, Dam diet E, Dam diet P:NP, Offspr. age","Offspr. sex, Dam diet during lactation, Dam diet E, Dam diet P:NP, Offspr. age"), RandomEffects = c("Random Effects","Study, Strain","Strain","Study, Strain","Study, Strain"))
join_table <- cbind(params_table, heter_table) 
models_table <- rbind(models_table, join_table)
#models_table
write.csv(models_table, "models_table.csv")
```

Summary (stats) tables for all analyses

```{r all combine stats tables, eval=TRUE, echo=FALSE, include=TRUE, message=FALSE, results='asis'}
##RI2_full stats table
stats_table <- table_null_RI2_full[3:4,]
stats_table <- rbind(stats_table, table_strain_RI2_full[4:11,])
stats_table <- rbind(stats_table, table_full1_RI2_full[4:12,])
stats_table <- rbind(stats_table, table_full2_RI2_full[4:11,])
stats_table <- rbind(stats_table, table_null_RI2_full[6:8,])
stats_table <- rbind(stats_table, table_strain_RI2_full[13:14,])
stats_table <- rbind(stats_table, table_full1_RI2_full[14:16,])
stats_table <- rbind(stats_table, table_full2_RI2_full[13:15,])
stats_table <- cbind(Model = c(" ", "1 (null)","2 (strain)",rep(" ", 7),"3 (full)",rep(" ", 8),"4 (full-alternative)", rep(" ", 7),"1 (null)", rep(" ", 2),"2 (strain)", rep(" ", 1), "3 (full)", rep(" ", 2), "4 (full-alternative)", rep(" ", 2)), stats_table)
join_table <- cbind(Data = c(" ", "Food Intake  full data set",rep(" ", nrow(stats_table)-2)), stats_table)
results_table <- join_table

##RI2_chow stats table
stats_table <- table_null_RI2_chow[4,]
stats_table <- rbind(stats_table, table_strain_RI2_chow[4:11,])
stats_table <- rbind(stats_table, table_full1_RI2_chow[4:10,])
stats_table <- rbind(stats_table, table_full2_RI2_chow[4:9,])
stats_table <- rbind(stats_table, table_null_RI2_chow[6:8,])
stats_table <- rbind(stats_table, table_strain_RI2_chow[13:14,])
stats_table <- rbind(stats_table, table_full1_RI2_chow[12:14,])
stats_table <- rbind(stats_table, table_full2_RI2_chow[11:13,])
stats_table <- cbind(Model = c("1 (null)","2 (strain)",rep(" ", 7),"3 (full)",rep(" ", 6),"4 (full-alternative)", rep(" ", 5),"1 (null)", rep(" ", 2),"2(strain)", rep(" ", 1), "3 (full)", rep(" ", 2), "4 (full-alternative)", rep(" ", 2)), stats_table)
join_table <- cbind(Data = c("Food Intake  chow data subset",rep(" ", nrow(stats_table)-1)), stats_table)
results_table <- rbind(results_table, join_table)

##BW_full stats table
stats_table <- table_null_BW_full[4,]
stats_table <- rbind(stats_table, table_strain_BW_full[4:11,])
stats_table <- rbind(stats_table, table_full1_BW_full[4:12,])
stats_table <- rbind(stats_table, table_full2_BW_full[4:11,])
stats_table <- rbind(stats_table, table_null_BW_full[6:8,])
stats_table <- rbind(stats_table, table_strain_BW_full[13:14,])
stats_table <- rbind(stats_table, table_full1_BW_full[14:16,])
stats_table <- rbind(stats_table, table_full2_BW_full[13:15,])
stats_table <- cbind(Model = c("1 (null)","2 (strain)",rep(" ", 7),"3 (full)",rep(" ", 8),"4(full-alternative)", rep(" ", 7),"1 (null)", rep(" ", 2),"2 (strain)", rep(" ", 1), "3 (full)", rep(" ", 2), "4(full-alternative)", rep(" ", 2)), stats_table)
join_table <- cbind(Data = c("Body Mass  full data set",rep(" ", nrow(stats_table)-1)), stats_table)
results_table <- rbind(results_table, join_table)

##BW_chow stats table
stats_table <- table_null_BW_chow[4,]
stats_table <- rbind(stats_table, table_strain_BW_chow[4:11,])
stats_table <- rbind(stats_table, table_full1_BW_chow[4:10,])
stats_table <- rbind(stats_table, table_full2_BW_chow[4:9,])
stats_table <- rbind(stats_table, table_null_BW_chow[6:8,])
stats_table <- rbind(stats_table, table_strain_BW_chow[13:14,])
stats_table <- rbind(stats_table, table_full1_BW_chow[12:14,])
stats_table <- rbind(stats_table, table_full2_BW_chow[11:13,])
stats_table <- cbind(Model = c("1 (null)","2 (strain)",rep(" ", 7),"3 (full)",rep(" ", 6),"4 (full-alternative)", rep(" ", 5),"1 (null)", rep(" ", 2),"2 (strain)", rep(" ", 1), "3 (full)", rep(" ", 2), "4 (full-alternative)", rep(" ", 2)), stats_table)
join_table <- cbind(Data = c("Body Mass  chow data subset",rep(" ", nrow(stats_table)-1)), stats_table)
results_table <- rbind(results_table, join_table)

dim(results_table)
results_table

write.csv(results_table, "results_table.csv")
```

##### ADDITIONAL ANALYSES

Offspring absolute food intake (AI)
-----------------------------------------------------

Calculate adjusted Hd variance values for experiments with shared control group.  

```{r AI shared controls adj Var, echo=FALSE}
# calculate variance of Hd adjusted for shared control 
data$AbsIntake_Hd_Var_adj <- 1/data$AbsIntake_N_exp + 1/data$AbsIntake_N_contr + data$AbsIntake_Hd^2/(2*data$AbsIntake_N_total)
# use normal variance of Hd for non-shared ES, and adjusted version for shared ES
data$AbsIntake_Hd_Var_combined <- ifelse(data$control_id %in% data$control_id[duplicated(data$control_id)], data$AbsIntake_Hd_Var_combined <- 1/data$AbsIntake_N_exp + 1/data$AbsIntake_N_contr + data$AbsIntake_Hd^2/(2*data$AbsIntake_N_total), data$AbsIntake_Hd_Var_combined <- ((data$AbsIntake_N_contr+data$AbsIntake_N_exp)/(data$AbsIntake_N_contr*data$AbsIntake_N_exp)) + ((data$AbsIntake_Hd^2)/(2*(data$AbsIntake_N_contr+data$AbsIntake_N_exp-2))))
```

Create variance-covariance matrices for absolute food intake effect sizes 

```{r AI shared controls matrix, echo=FALSE }
library(Matrix)
# find start and end coordinates for the subsets
shared_coord <- which(data$control_id %in% data$control_id[duplicated(data$control_id)]==TRUE)
#shared_coord

# matrix of combinations of coordinates for each experiment with shared control
combinations <- do.call("rbind", tapply(shared_coord, data[shared_coord,"control_id"], function(x) t(combn(x,2))))
#combinations

# create square matrix matching N of ES, filled with zeros
AbsIntake_matrix <- matrix(0, nrow = dim(data)[1],ncol = dim(data)[1])
rownames(AbsIntake_matrix) <- data$ES_ID
colnames(AbsIntake_matrix) <- data$ES_ID

# calculate covariance values between Hd values at the positions in shared_list and place them on the matrix
for (i in 1:dim(combinations)[1]){
  p1 <- combinations[i,1]
  p2 <- combinations[i,2]
  p1_p2_cov <- 1/data[p1,"AbsIntake_N_contr"] + (data[p1,"AbsIntake_Hd"]*data[p2,"AbsIntake_Hd"]) / (2*data[p1,"AbsIntake_N_total"])
  AbsIntake_matrix[p1,p2] <- p1_p2_cov
  AbsIntake_matrix[p2,p1] <- p1_p2_cov
}

# add the diagonal - use data$AbsIntake_Hd_Var_combined as matrix diagonal
diag(AbsIntake_matrix) <- data$AbsIntake_Hd_Var_combined

#save the matrices as an R data objects
save(AbsIntake_matrix, file = "AI_VC_matrix.RData")
#load(file = "AI_VC_matrix.RData")
```

Define full dataset variables.
```{r AI full data, echo=FALSE, eval=TRUE, include=FALSE}
d <- data$AbsIntake_Hd
vofd <- data$AbsIntake_Hd_Var_combined
m <- AbsIntake_matrix
AinvG <- solve(m)
AnivG <- as(AinvG,"dgCMatrix")
```

# AI - Null model for the full data set.

Run models.
```{r null model AI full data, echo=FALSE, eval=FALSE, include=FALSE}
##long runs
prior3 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=.002),G2=list(V=1,nu=.002),G3=list(V=1,fix=1))) #inverse-Gamma prior with AnivG
model_null_AI_full_1 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_null_AI_full_2 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_null_AI_full_3 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
save(model_null_AI_full_1,model_null_AI_full_2,model_null_AI_full_3,file="model_null_AI_full.RData") 
```

Get results.
```{r null model AI full data results, echo=FALSE, eval=TRUE, include=FALSE}
load("model_null_AI_full.RData")
m1 <- model_null_AI_full_1
m2 <- model_null_AI_full_2
m3 <- model_null_AI_full_3

#check model convergence
gelman.diag(list(m1$Sol[,1],m2$Sol[,1],m3$Sol[,1])) #The shrink factors should be below 1.05
gelman.diag(list(m1$VCV[,c(1,2)],m2$VCV[,c(1,2)],m3$VCV[,c(1,2)]))
gelman.diag(list(m1$Deviance,m2$Deviance,m3$Deviance))
#check chain autocorrelation
autocorr(m1$Sol[,c(4)])
autocorr(m1$VCV[,c(1:2)])
autocorr(m2$Sol[,c(4)])
autocorr(m2$VCV[,c(1:2)])
autocorr(m3$Sol[,c(4)])
autocorr(m3$VCV[,c(1:2)])
#extract and summarise DIC
print(c(m1$DIC,m2$DIC,m3$DIC))
mean(c(m1$DIC, m2$DIC, m3$DIC)) 
range(c(m1$DIC, m2$DIC, m3$DIC))  

chosen <- m3

plot(chosen)
summary(chosen)

### heterogeneity and variances
WI <- na.omit(1/data$Bodyweight_Hd_Var_adj) 
s2I <- sum(WI*(length(WI)-1))/(sum(WI)^2-sum(WI^2)) # typical sampling (measurement) error variance (sigma2m)
total_var <- chosen$VCV[,"Study_ID"]+chosen$VCV[,"Strain"]+chosen$VCV[,"units"]+s2I # total variance (sigma2t)
total_het <- (total_var-s2I)/total_var # total heterogeneity I2
#for pasting into Excel table
Study_ID <- round(c(summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Study_ID"]/total_var)*100),1)
Strain <- round(c(summary(chosen$VCV[,"Strain"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Strain"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Strain"]/total_var)*100),1)
units <- round(c(summary(chosen$VCV[,"units"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"units"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"units"]/total_var)*100),1)
total <- round(c(summary(total_het)$statistics[1]*100,summary(total_het)$statistics[2]*100,posterior.mode(total_het)*100),1)
res_df <- t(data.frame(Study_ID=Study_ID,Strain=Strain,units=units,total=total))
# version with mean and range for DIC
res_df <- format(res_df, nsmall = 2)
DICs <- c(m1$DIC, m2$DIC, m3$DIC)
DICmean <- format(round(mean(DICs),2), nsmall = 2)
DICrange <- paste0(format(round(range(DICs)[1],2), nsmall = 2)," - ",format(round(range(DICs)[2],2), nsmall = 2))
res_df <- t(c(paste0(DICmean, "(", DICrange, ")"),
            paste0(res_df[1,1],"(",res_df[1,2],")[",res_df[1,3],"]"),
            paste0(res_df[2,1],"(",res_df[2,2],")[",res_df[2,3],"]"),
            paste0(res_df[3,1],"(",res_df[3,2],")[",res_df[3,3],"]"),
            paste0(res_df[4,1],"(",res_df[4,2],")[",res_df[4,3],"]")))
colnames(res_df) <- c("DIC (DIC range)","I2study","I2strain","I2residual","I2total")
rownames(res_df) <- "mean(SD)[mode]"
write.csv(res_df,"results_table_model_null_AI_full.csv")

### fixed effects (overall intercept)
interc <- c(posterior.mode(chosen$Sol[,1]),summary(chosen$Sol[,1])$statistics[1],summary(chosen$Sol)$statistics[2],HPDinterval(chosen$Sol[,1])[1],HPDinterval(chosen$Sol[,1])[2])
interc <- as.data.frame(t(interc))
rownames(interc) <- c("intercept")
write.table(t(c("Fixed effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_null_AI_full.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(round(interc,3),"results_table_model_null_AI_full.csv", sep=",", col.names = FALSE, append = TRUE)

### random effects
Mode <- posterior.mode(chosen$VCV)
Mean <- summary(chosen$VCV)$statistics[,1]
SD <- summary(chosen$VCV)$statistics[,2]
Lower <- HPDinterval(chosen$VCV)[,1]
Upper <- HPDinterval(chosen$VCV)[,2]
res_df <- data.frame(Mode=Mode,Mean=Mean,SD=SD,Lower=Lower,Upper=Upper)
res_df <- res_df[-(dim(res_df)[1]-1),]
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Study_ID","Strain","residuals")
write.table(t(c("Random effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_null_AI_full.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_null_AI_full.csv", sep=",", col.names = FALSE, append = TRUE)
```

Table.
```{r null model AI full data table, eval=TRUE, echo=FALSE, include=TRUE, message=FALSE, results='asis'}
table <- read.table("results_table_model_null_AI_full.csv", sep=",")
#table
kable(table, digits = 3)
```


Offspring linearly-adjusted food intake (RI)
-----------------------------------------------------

Calculate adjusted Hd variance values for experiments with shared control group.  

```{r RI shared controls adj Var, echo=FALSE}
# calculate variance of Hd adjusted for shared control 
data$RelIntake_Hd_Var_adj <- 1/data$AbsIntake_N_exp + 1/data$AbsIntake_N_contr + data$RelIntake_Hd^2/(2*data$AbsIntake_N_total)
# use normal variance of Hd for non-shared ES, and adjusted version for shared ES
data$RelIntake_Hd_Var_combined <- ifelse(data$control_id %in% data$control_id[duplicated(data$control_id)], data$RelIntake_Hd_Var_combined <- 1/data$AbsIntake_N_exp + 1/data$AbsIntake_N_contr + data$RelIntake_Hd^2/(2*data$AbsIntake_N_total), data$RelIntake_Hd_Var_combined <- ((data$AbsIntake_N_contr+data$AbsIntake_N_exp)/(data$AbsIntake_N_contr*data$AbsIntake_N_exp)) + ((data$RelIntake_Hd^2)/(2*(data$AbsIntake_N_contr+data$AbsIntake_N_exp-2))))
```

Create variance-covariance matrices for absolute food intake effect sizes 

```{r RI shared controls matrix, echo=FALSE }
library(Matrix)
# find start and end coordinates for the subsets
shared_coord <- which(data$control_id %in% data$control_id[duplicated(data$control_id)]==TRUE)
#shared_coord

# matrix of combinations of coordinates for each experiment with shared control
combinations <- do.call("rbind", tapply(shared_coord, data[shared_coord,"control_id"], function(x) t(combn(x,2))))
#combinations

# create square matrix matching N of ES, filled with zeros
RelIntake_matrix <- matrix(0, nrow = dim(data)[1],ncol = dim(data)[1])
rownames(RelIntake_matrix) <- data$ES_ID
colnames(RelIntake_matrix) <- data$ES_ID

# calculate covariance values between Hd values at the positions in shared_list and place them on the matrix
for (i in 1:dim(combinations)[1]){
  p1 <- combinations[i,1]
  p2 <- combinations[i,2]
  p1_p2_cov <- 1/data[p1,"RelIntake_N_contr"] + (data[p1,"RelIntake_Hd"]*data[p2,"RelIntake_Hd"]) / (2*data[p1,"AbsIntake_N_total"])
  RelIntake_matrix[p1,p2] <- p1_p2_cov
  RelIntake_matrix[p2,p1] <- p1_p2_cov
}

# add the diagonal - use data$RelIntake_Hd_Var_combined as matrix diagonal
diag(RelIntake_matrix) <- data$RelIntake_Hd_Var_combined

#save the matrices as an R data objects
save(RelIntake_matrix, file = "RI_VC_matrix.RData")
#load(file = "RI_VC_matrix.RData")
```

Define full dataset variables.
```{r RI full data, echo=FALSE, eval=TRUE, include=FALSE}
d <- data$RelIntake_Hd
vofd <- data$RelIntake_Hd_Var_combined
m <- RelIntake_matrix
RInvG <- solve(m)
AnivG <- as(RInvG,"dgCMatrix")
```

# RI - Null model for the full data set.

Run models.
```{r null model RI full data, echo=FALSE, eval=FALSE, include=FALSE}
##long runs
prior3 <- list(R=list(V=1,nu=.002),G=list(G1=list(V=1,nu=.002),G2=list(V=1,nu=.002),G3=list(V=1,fix=1))) #inverse-Gamma prior with AnivG
model_null_RI_full_1 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_null_RI_full_2 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
model_null_RI_full_3 <- MCMCglmm(d~1,random=~Study_ID+Strain+ES_ID,family="gaussian",data=data,ginverse=list(ES_ID=AnivG), verbose=T,nitt=1100000,thin=1000,burnin=100000,pr=T,prior=prior3)
save(model_null_RI_full_1,model_null_RI_full_2,model_null_RI_full_3,file="model_null_RI_full.RData") 
```

Get results.
```{r null model RI full data results, echo=FALSE, eval=TRUE, include=FALSE}
load("model_null_RI_full.RData")
m1 <- model_null_RI_full_1
m2 <- model_null_RI_full_2
m3 <- model_null_RI_full_3

#check model convergence
gelman.diag(list(m1$Sol[,1],m2$Sol[,1],m3$Sol[,1])) #The shrink factors should be below 1.05
gelman.diag(list(m1$VCV[,c(1,2)],m2$VCV[,c(1,2)],m3$VCV[,c(1,2)]))
gelman.diag(list(m1$Deviance,m2$Deviance,m3$Deviance))
#check chRIn autocorrelation
autocorr(m1$Sol[,c(4)])
autocorr(m1$VCV[,c(1:2)])
autocorr(m2$Sol[,c(4)])
autocorr(m2$VCV[,c(1:2)])
autocorr(m3$Sol[,c(4)])
autocorr(m3$VCV[,c(1:2)])
#extract and summarise DIC
print(c(m1$DIC,m2$DIC,m3$DIC))
mean(c(m1$DIC, m2$DIC, m3$DIC)) 
range(c(m1$DIC, m2$DIC, m3$DIC))  

chosen <- m2

plot(chosen)
summary(chosen)

### heterogeneity and variances
WI <- na.omit(1/data$Bodyweight_Hd_Var_adj) 
s2I <- sum(WI*(length(WI)-1))/(sum(WI)^2-sum(WI^2)) # typical sampling (measurement) error variance (sigma2m)
total_var <- chosen$VCV[,"Study_ID"]+chosen$VCV[,"Strain"]+chosen$VCV[,"units"]+s2I # total variance (sigma2t)
total_het <- (total_var-s2I)/total_var # total heterogeneity I2
#for pasting into Excel table
Study_ID <- round(c(summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Study_ID"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Study_ID"]/total_var)*100),1)
StrRIn <- round(c(summary(chosen$VCV[,"Strain"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"Strain"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"Strain"]/total_var)*100),1)
units <- round(c(summary(chosen$VCV[,"units"]/total_var)$statistics[1]*100,summary(chosen$VCV[,"units"]/total_var)$statistics[2]*100,posterior.mode(chosen$VCV[,"units"]/total_var)*100),1)
total <- round(c(summary(total_het)$statistics[1]*100,summary(total_het)$statistics[2]*100,posterior.mode(total_het)*100),1)
res_df <- t(data.frame(Study_ID=Study_ID,Strain=Strain,units=units,total=total))
# version with mean and range for DIC
res_df <- format(res_df, nsmall = 2)
DICs <- c(m1$DIC, m2$DIC, m3$DIC)
DICmean <- format(round(mean(DICs),2), nsmall = 2)
DICrange <- paste0(format(round(range(DICs)[1],2), nsmall = 2)," - ",format(round(range(DICs)[2],2), nsmall = 2))
res_df <- t(c(paste0(DICmean, "(", DICrange, ")"),
            paste0(res_df[1,1],"(",res_df[1,2],")[",res_df[1,3],"]"),
            paste0(res_df[2,1],"(",res_df[2,2],")[",res_df[2,3],"]"),
            paste0(res_df[3,1],"(",res_df[3,2],")[",res_df[3,3],"]"),
            paste0(res_df[4,1],"(",res_df[4,2],")[",res_df[4,3],"]")))
colnames(res_df) <- c("DIC (DIC range)","I2study","I2strain","I2residual","I2total")
rownames(res_df) <- "mean(SD)[mode]"
write.csv(res_df,"results_table_model_null_RI_full.csv")

### fixed effects (overall intercept)
interc <- c(posterior.mode(chosen$Sol[,1]),summary(chosen$Sol[,1])$statistics[1],summary(chosen$Sol)$statistics[2],HPDinterval(chosen$Sol[,1])[1],HPDinterval(chosen$Sol[,1])[2])
interc <- as.data.frame(t(interc))
rownames(interc) <- c("intercept")
write.table(t(c("Fixed effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_null_RI_full.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(round(interc,3),"results_table_model_null_RI_full.csv", sep=",", col.names = FALSE, append = TRUE)

### random effects
Mode <- posterior.mode(chosen$VCV)
Mean <- summary(chosen$VCV)$statistics[,1]
SD <- summary(chosen$VCV)$statistics[,2]
Lower <- HPDinterval(chosen$VCV)[,1]
Upper <- HPDinterval(chosen$VCV)[,2]
res_df <- data.frame(Mode=Mode,Mean=Mean,SD=SD,Lower=Lower,Upper=Upper)
res_df <- res_df[-(dim(res_df)[1]-1),]
res_df <- format(round(res_df,3), nsmall = 3)
rownames(res_df) <- c("Study_ID","Strain","residuals")
write.table(t(c("Random effects","Mode","Mean","SD","Lower","Upper")),"results_table_model_null_RI_full.csv", sep=",", col.names = FALSE, row.names = FALSE, append = TRUE)
write.table(res_df,"results_table_model_null_RI_full.csv", sep=",", col.names = FALSE, append = TRUE)
```

Table.
```{r null model RI full data table, eval=TRUE, echo=FALSE, include=TRUE, message=FALSE, results='asis'}
table <- read.table("results_table_model_null_RI_full.csv", sep=",")
#table
kable(table, digits = 3)
```



TO DO NEXT
----------
*Publication bias tests
*final figures for the MS: funnel, forest, bubble plots